### 2022-06-20 paper/main.tex
atomic data implemented GUI to do

\documentclass[reprint, amsmath, amssymb, aps, prl]{revtex4-2}

\usepackage{graphicx}
\graphicspath{{./assets/figures/}}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage[table]{xcolor}
\usepackage{empheq} % to use left braces for list of equations
\usepackage{hyperref}

\begin{document}

\preprint{APS/123-QED}

\title{Ground state energy of diatomic molecules\\ in the Quantum Drude Oscillator model}
%\thanks{}

\author{Matthieu Sarkis}
\email{matthieu.sarkis@uni.lu}

\author{Loris di Cairano}%
\email{loris.dicairano@uni.lu}

\author{Alexandre Tkatchenko}%
\email{alexandre.tkatchenko@uni.lu}

\affiliation{
Department of Physics and Materials Science\\ University of Luxembourg, L-1511, Luxembourg City, Luxembourg.
}

%\collaboration{}%\noaffiliation

\date{\today}

\begin{abstract}
Abstract
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item.
%\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{Introduction}

    A Quantum Drude Oscillator (QDO) is a very simple atomistic model in which the properties of an atom are encompassed in a small number of parameters. The model consists in assimilating the atom to a point particle of mass $m$ and electric charge $-q$ attached to a fixed (infinite mass) center of charge $+q$ by a harmonic spring characterized by a frequency $\omega$. Molecules are then defined as a collections of QDOs interactig through Coulomb interactions.

    \begin{figure}[h!]
    \centering
        \includegraphics[scale=0.49]{QDOs}
        \caption{\label{fig:epsart} Pair of interacting QDOs.}
    \end{figure}

    This simple model has been extensively used in various contexts, for instance in order to tackle the electronic structure problem for isolated molecules, in particular long range interactions, as well as to study the impact of an ambient bath or of an external electric field on molecular properties \cite{Karimpour_2022}.

    Even though the harmonic oscillator nature of the atomic constituents in this model drastically simplify the complexity of problem, the all-body Coulomb interaction remains challenging. One possible way to proceed is to treat the Coulomb interaction by performing a multipolar expansion.

    By truncating the multipolar expansion up to Dipole-Dipole, one obtain a quadratic Hamiltonian, hence the quantum Hamiltonian can be analytically diagonalized. Though simple, this system was shown to capture long-range phenomena in large atomistic systems \cite{https://doi.org/10.48550/arxiv.2205.11549}.

    In the present work, we focus instead on small (diatomic) molecules in 1d, and treat in an \textit{analytical} way the Coulombic interactions up to Quadrupole-Quadrupole and Dipole-Octupole order, paving the way towards generalization for larger systems.

    \textit{GitHub repository}: The reader will find an open source code accompanying this paper following this \href{https://github.com/MatthieuSarkis/Quartic-Potential}{link}.

\section{Quartic Hamiltonian for diatomic molecules}

    \subsection{Multipolar expansion for the Coulomb potential}

        The Hamiltonian describing a system of $N$ QDOs in 3d is given by:
        \begin{equation}
        \label{eq:full_QDO_Hamiltonian}
            H=\sum_{i=1}^N\left[\frac{1}{2}m_i\dot{\vec x}_i^2 + \frac{1}{2}m_i\omega_i^2\vec x_i^2\right] +\sum_{i<j}V_\text{Coul}\left(\vec x_i, \vec x_j\right)\,,
        \end{equation}
        with the Coulomb interaction given by
        \begin{equation*}
            \frac{V_\text{Coul}\left(\vec x_1, \vec x_2\right)}{q_1q_2(4\pi\epsilon_0)^{-1}}=\frac{1}{r} - \frac{1}{|\vec r + \vec x_1|} - \frac{1}{|\vec r - \vec x_2|} + \frac{1}{|\vec r - \vec x_2 + \vec x_1|}
        \end{equation*}
        In the multipolar expansion, this can be expressed as:
        \begin{equation}
            V_\text{Coul}\left(\vec x_1, \vec x_2\right)= \sum_{n\geq 0} V_n\left(\vec x_1, \vec x_2\right)\,,
        \end{equation}
        with the following scaling behavior in terms of the distance between the centers:
        \begin{equation}
            V_n\left(\vec x_1, \vec x_2\right)\propto r^{-n+3}\,.
        \end{equation}
        The first terms in that multipolar expansion have the following interpretation:
        \begin{itemize}
            \item $n=0$ : Dipole-Dipole interaction (DD),
            \item $n=1$ : Dipole-Quadrupole interaction (DQ),
            \item $n=2$ : Quadrupole-Quadrupole and Dipole-Octupole interaction (QQ+DO).
        \end{itemize}
        Using the following identity for generic vectors $\vec r$ and $\vec \epsilon$:
        \begin{widetext}
        \begin{equation}
            \frac{1}{\left|\vec r - \vec\epsilon\,\right|} = \frac{1}{r}\left[1 + \frac{\vec\epsilon\cdot\hat r}{r} - \frac{\epsilon^2 - 3(\vec\epsilon\cdot\hat r)^2}{2r^2}+\frac{5(\vec\epsilon\cdot\hat r)^3-3\epsilon^2(\vec\epsilon\cdot\hat r)}{2r^3}+\frac{35(\vec\epsilon\cdot\hat r)^4-30\epsilon^2(\vec\epsilon\cdot\hat r)^2+3\epsilon^4}{8r^4}+\mathcal O\left(\frac{\epsilon^5}{r^5}\right)\right]
        \end{equation}
        \end{widetext}
        one can explicitely compute $V_0$, $V_1$ and $V_2$. Instead of writting out the expression of these potentials in full glory, let us now restrict ourselves to a system composed of $N=2$ QDOs.

    \subsection{Reduced particle system}

        Let us move to the center of mass frame, in which the dynamics reduces to that of an effective reduced particle:
        \begin{subequations}
        \begin{align}
            &\vec x:=\vec x_1 - \vec x_2\\
            &m_1\vec x_1 + m_2\vec x_2 = \vec 0\,.
        \end{align}
        \end{subequations}
        In terms of the reduced variable, a straightforward computation gives us:
        \begin{subequations}
        \begin{align}
            V_0(\vec x)=\,&-\frac{m_1m_2}{(m_1+m_2)^2}\cdot\frac{ x^2-3(\vec x\cdot\hat r)^2}{4\pi\epsilon_0r^3}\,,\\
            V_1(\vec x)=\,&\frac{3m_1m_2}{2(m_1+m_2)^2}\cdot\frac{(\vec x\cdot\hat r)\left(3x^2 - 5(\vec x\cdot\hat r)^2\right)}{4\pi\epsilon_0r^4}\,,\\
            V_2(\vec x)=\,&\frac{m_1m_2(2m_1^2+3m_1m_2+2m_2^2)}{4(m_1+m_2)^4}\times\\
            &\times\frac{3x^4 - 30(\vec x\cdot\hat r)^2 x^2+35(\vec x\cdot\hat r)^4}{4\pi\epsilon_0r^5}\nonumber\,.
        \end{align}
        \end{subequations}
        Let us now assume that the system is effectively one-dimensional, aligned along the direction on which the centers of the two QDOs are sitting. One obtain the following one-dimensional potentials for an effective particle of mass $m_1m_2 / (m_1+m_2)$:
        \begin{subequations}
        \begin{align}
            V_0(x)&=\frac{2m_1m_2}{(m_1+m_2)^2}\cdot\frac{2 x^2}{4\pi\epsilon_0r^3}\,,\\
            V_1(x)&=-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{\text{sgn}(\vec x\cdot\hat r)|x|x^2}{4\pi\epsilon_0r^4}=\mathbin{\textcolor{teal}{-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{x^3}{4\pi\epsilon_0r^4}}}\,,\\
            V_2(x)&=\frac{2m_1m_2(2m_1^2+3m_1m_2+2m_2^2)}{(m_1+m_2)^4}\cdot\frac{x^4}{4\pi\epsilon_0r^5}\,.
        \end{align}
        \end{subequations}

        \textcolor{teal}{As a comment concerning this possible sign issue: maybe one can argue that provided the external field is strong enough, we can take $x^3$.}

        Including the contribution of the harmonic potentials present in (\ref{eq:full_QDO_Hamiltonian}) and coupling the system to an external electric field, one finally obtain the following total one-dimensional potential:
        \begin{equation}
        \label{eq:quartic_potential}
            V(x) = \alpha x + \beta x^2 + \gamma x^3 + \delta x^4 \,,
        \end{equation}
        with the following expression of the coupling constants:
        \begin{subequations}
        \label{eq:coupling_constants}
        \begin{align}
            \alpha &= -\frac{m_1 q_2 + m_2 q_1}{m_1+m_2}\cdot \mathcal E\\
            \beta &= \frac{m_1m_2}{(m_1+m_2)^2}\cdot\frac{2q_1 q_2}{4\pi\epsilon_0r^3} + \frac{1}{2}\cdot\frac{m_1m_2}{m_1+m_2}\cdot\frac{m_1\omega_2^2+m_2\omega_1^2}{m_1+m_2}\\
            \gamma&=-\frac{m_1m_2}{(m_1+m_2)^2}\cdot\frac{3 q_1 q_2}{4\pi\epsilon_0r^4}\,,\\
            \delta&=\frac{2m_1m_2(2m_1^2+3m_1m_2+2m_2^2)}{(m_1+m_2)^4}\cdot\frac{q_1 q_2}{4\pi\epsilon_0r^5}\,.
        \end{align}
        \end{subequations}

\section{Analytic solution of the Schr\"odinger equation}

    In what follows, we define $k^2:=\frac{m_1+m_2}{m_1 m_2}\frac{\hbar^2}{2}$.
    Let us consider the time-independent Schr\"odinger equation
    \begin{equation}
        \left[\frac{\text{d}^2}{\text{d}x^2} + \frac{\epsilon - V(x)}{k^2}\right]\psi(x) = 0\,,
    \end{equation}
    where the potential $V$ is provided by (\ref{eq:quartic_potential}) and (\ref{eq:coupling_constants}).
    Performing the following change of variable:
    \begin{equation}
        \psi(x)=\exp\left[\frac{\gamma^2-4\beta\delta}{8k\delta^{3/2}}\,x-\frac{\gamma}{4k\delta^{1/2}}\,x^2-\frac{\delta^{1/2}}{3k}\,x^3\right]\phi(x)
    \end{equation}
    we obtain:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &\frac{\text{d}^2\phi}{\text{d}x^2}(x)+\left[\frac{\gamma^2-4\beta\delta}{4k\delta^{3/2}}-\frac{\gamma}{k\delta^{1/2}}\,x-\frac{2\delta^{1/2}}{k}\,x^2\right]\frac{\text{d}\phi}{\text{d}x}(x)\\
        &+\left[\frac{16 \delta ^2 \left(\beta ^2+4 \delta  \epsilon \right)-8 \beta  \gamma ^2 \delta +\gamma ^4-32 \gamma  \delta ^{5/2} k}{64 \delta ^3 k^2}-\frac{8 \alpha  \delta ^2-4 \beta  \gamma  \delta +\gamma ^3+16 \delta ^{5/2} k}{8 \delta ^2 k^2}\,x\right]\phi(x)=0\,,
    \end{split}
    \end{equation}
    \end{widetext}
    which is known as the so-called \textit{tri-confluent Heun equation}.
    We further perform the following change of variable, the reason why to become clear soon:
    \begin{equation}
        \phi(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f(x)\,,
    \end{equation}
    as well as map the positive real axis to the segment $[0,1]$ through the change of argument
    \begin{equation}
        z=\frac{x}{x+1}\,,
    \end{equation}
    and look for a solution of the obtained ODE in terms of a series expansion at zero of the form:
    \begin{equation}
        f(z)=\sum_{n\geq 0}c_nz^n\,.
    \end{equation}
    Plugging the ansatz into the differential equation, we obtain the following recurrence relation between the coefficients:
    \begin{widetext}
    \begin{equation}
    \begin{split}
        &(n+1)(n+2) c_{n+2}+(n+1)(A -4n)c_{n+1} +[6(n-1) n+B n+E]c_n \\
        &+[C (n-1)+F-4(n-2) (n-1)]c_{n-1} + [(n-3) (n-2)+D (n-2)+G]c_{n-2}=0\ \ \ (n\geq 2)
    \end{split}
    \end{equation}
    \end{widetext}
    where the various coefficients are listed in full details in appendix. The coefficients $c_0$ and $c_1$ are to be fixed through boundary conditions, and the coeffients $c_2$ and $c_3$ are in turn fixed by the following relations
    \begin{equation}
    \begin{split}
        c_2&=-Ec_0-Ac_1\,,\\
        c_3&=-\frac{ F c_0+(B+E)c_1 +2 (A-4)c_2 }{6}\,.
    \end{split}
    \end{equation}

%\begin{acknowledgments}
%We wish to acknowledge ...
%\end{acknowledgments}

\newpage

\appendix

\section{Details on the derivation}

    \begin{widetext}
    \begin{equation*}
    \begin{split}
        &A=-\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (2 \beta +\gamma )+\gamma ^3+32 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &B=\frac{8 \delta ^2 (3 \alpha +2 \beta -\gamma )-4 \gamma  \delta  (3 \beta +\gamma )+3 \gamma ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &C=-\frac{8 \delta ^2 (3 \alpha +\beta -\gamma )-2 \gamma  \delta  (6 \beta +\gamma )+3 \gamma ^3+16 \delta ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
        &D=\frac{-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)}{8 \delta ^{5/2} k}\\
        &E=\frac{4 \gamma ^2 \delta ^2 \left(\gamma  (4 \alpha +\gamma )+4 \beta ^2+8 \beta  \gamma \right)-32 \gamma  \delta ^3 (\alpha +\beta ) (2 \beta +\gamma )+64 \delta ^4 (\alpha +\beta )^2-4 \gamma ^4 \delta  (2 \beta +\gamma )+\gamma ^6+256 \delta ^5 \left(2 k^2+\epsilon \right)+128 \delta ^{9/2} k (3 \alpha +2 \beta -\gamma )-64 \gamma  \delta ^{7/2} k (3 \beta +\gamma )+48 \gamma ^3 \delta ^{5/2} k}{256 \delta ^5 k^2}\\
        &F=-\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \gamma  \delta  (\beta +2 \delta )+\gamma ^3-2 \gamma ^2 \delta +8 \delta ^2 \left(\alpha +\beta +2 \delta +4 \sqrt{\delta } k\right)\right)}{128 \delta ^5 k^2}\\
        &G=\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)\right)}{256 \delta ^5 k^2}
    \end{split}
    \end{equation*}
    \end{widetext}

\begin{table}[b]
\caption{\label{tab:table2} aaa}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}

\nocite{*}
\bibliography{bibliography}

\end{document}

### 2022-06-20 bash_scripts/main.sh

@@ -1,11 +1,7 @@
 python src/main.py \
-    --m1 1.0 \
-    --m2 1.0 \
-    --q1 1.0 \
-    --q2 1.0 \
-    --omega1 1.0 \
-    --omega2 1.0 \
-    --r 1.0 2.0 2.5 \
-    --tau 1.0 \
+    --atom1 He \
+    --atom2 He \
+    --r 1.0 2.0 \
+    --tau 0.0 \
     --epsilon0 1.0 \
     --S0 -1.0

### 2022-06-20 src/engine/main.py

@@ -1,0 +1,61 @@
+from argparse import ArgumentParser
+import os
+
+#from src.solver import Solver
+from src.engine.solver_v2 import Solver
+
+def main(args) -> None:
+
+    log_dir = './results'
+    os.makedirs(log_dir, exist_ok=True)
+
+    solver = Solver(
+        atom1=args.atom1,
+        atom2=args.atom2,
+        tau=args.tau,
+        r=args.r,
+        epsilon0=args.epsilon0,
+        S0=args.S0,
+        energy_unit=args.energy_unit,
+        log_dir=log_dir
+    )
+
+    #solver = Solver(
+    #    m1=args.m1,
+    #    m2=args.m2,
+    #    q1=args.q1,
+    #    q2=args.q2,
+    #    omega1=args.omega1,
+    #    omega2=args.omega2,
+    #    tau=args.tau,
+    #    r=args.r,
+    #    epsilon0=args.epsilon0,
+    #    S0=args.S0,
+    #    log_dir=log_dir
+    #)
+
+    solver.solve()
+
+if __name__ == '__main__':
+
+    parser = ArgumentParser()
+
+    #parser.add_argument('--m1',     nargs='+', type=float, default=1.0,   help="Mass of QDO 1")
+    #parser.add_argument('--m2',     nargs='+', type=float, default=1.0,   help="Mass of QDO 2")
+    #parser.add_argument('--q1',     nargs='+', type=float, default=1.0,   help="Charge of QDO 1")
+    #parser.add_argument('--q2',     nargs='+', type=float, default=1.0,   help="Charge of QDO 2")
+    #parser.add_argument('--omega1', nargs='+', type=float, default=1.0,   help="Frequency of QDO 1")
+    #parser.add_argument('--omega2', nargs='+', type=float, default=1.0,   help="Frequency of QDO 2")
+
+    parser.add_argument('--atom1',             type=str,   default='H',       help='First atom in the diatomic molecule',  choices=['H', 'Li', 'K', 'Rb', 'Cs', 'He', 'Ne', 'Ar', 'Kr', 'Xe'])
+    parser.add_argument('--atom2',             type=str,   default='H',       help='second atom in the diatomic molecule', choices=['H', 'Li', 'K', 'Rb', 'Cs', 'He', 'Ne', 'Ar', 'Kr', 'Xe'])
+    parser.add_argument('--r',      nargs='+', type=float, default=1.0,       help="Distance between the two QDOs, measured in atomic units (multiple of Bohr radius)")
[…]

### 2022-06-20 src/engine/solver.py

@@ -5,11 +5,10 @@ import os
 from scipy.optimize import fsolve
 from typing import Dict, List
 
-from src.positive_coefficient import coefPlus
-from src.negative_formatted import minusPlus
+from src.expansion_coefficients.positive_coefficient import coefPlus
+from src.expansion_coefficients.negative_coefficient import coefMinus
 from src.couplings import *
-
-HBAR = 1
+from src.utils.atomic_data import HBAR
 
 class Solver():
 

### 2022-06-20 src/engine/solver_v2.py

@@ -1,0 +1,113 @@
+import itertools
+import json
+import numpy as np
+import os
+from scipy.optimize import fsolve
+from typing import Dict, List
+
+from src.engine.expansion_coefficients.positive_coefficient import coefPlus
+from src.engine.expansion_coefficients.negative_coefficient import coefMinus
+from src.engine.couplings import *
+from src.engine.utils.atomic_data import *
+
+class Solver():
+
+    def __init__(
+        self,
+        atom1: str,
+        atom2: str,
+        tau: List[float],
+        r: List[float],
+        epsilon0: float = 1.0,
+        S0: float = -10.0,
+        energy_unit: str = 'hartree',
+        log_dir: str = './results'
+    ) -> None:
+
+        self.atom1 = atom1
+        self.atom2 = atom2
+
+        self.m1 = ATOMIC_PARAMETERS[atom1]['m']
+        self.q1 = ATOMIC_PARAMETERS[atom1]['q']
+        self.omega1 = ATOMIC_PARAMETERS[atom1]['omega']
+        self.m2 = ATOMIC_PARAMETERS[atom2]['m']
+        self.q2 = ATOMIC_PARAMETERS[atom2]['q']
+        self.omega2 = ATOMIC_PARAMETERS[atom2]['omega']
+
+        self.tau = tau
+        self.r = r
+        self.x0 = [epsilon0, S0]
+        self.energy_unit = energy_unit
+
+        self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
+        os.makedirs(self.log_dir, exist_ok=True)
+
+        self.grid = self._prepare_grid()
+
+    def solve(self) -> List[float]:
+
+        for i in range(len(self.grid)):
+
+            alpha_ = alpha(self.m1, self.m2, self.q1, self.q2, self.grid[i]['tau'])
+            beta_ = beta(self.m1, self.m2, self.q1, self.q2, self.omega1, self.omega2, self.grid[i]['r'])
+            gamma_ = gamma(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
+            delta_ = delta(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
+            H = ((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2
+
+            x = fsolve(self.equations, self.x0, args=(alpha_, beta_, gamma_, delta_, H))
+
[…]

### 2022-06-20 src/engine/utils/atomic_data.py

@@ -1,0 +1,72 @@
+from typing import Tuple
+
+HBAR = 1.0
+
+# Obtained from "Quantum Drude Oscillators for Accurate Many-body Intermolecular Forces"
+DISPERSION_PARAMETERS = {
+    'H': {'alpha': 4.5, 'C6': 6.49, 'C8': 124.5},
+    'He': {'alpha': 1.38, 'C6': 1.46, 'C8': 14.05},
+    'Ne': {'alpha': 2.66, 'C6': 6.88, 'C8': 76},
+}
+
+# Obtained from "Quantum Drude oscillator model of atoms and molecules: Many-body polarization and dispersion interactions for atomistic simulation"
+# Those quantities are in atomic units (q_e = 1, m_e = 1, hbar = 1, Energy in Hartree)
+ATOMIC_PARAMETERS = {
+    'H':  {'omega': 0.4273, 'm': 0.6099, 'q': 0.7080},
+    'Li': {'omega': 0.0687, 'm': 1.2545, 'q': 0.9848},
+    'K':  {'omega': 0.0630, 'm': 0.8101, 'q': 0.9670},
+    'Rb': {'omega': 0.0603, 'm': 0.7343, 'q': 0.9274},
+    'Cs': {'omega': 0.0531, 'm': 0.6939, 'q': 0.8950},
+    'He': {'omega': 1.0187, 'm': 0.5083, 'q': 0.8532},
+    'Ne': {'omega': 1.2965, 'm': 0.3491, 'q': 1.2494},
+    'Ar': {'omega': 0.7272, 'm': 0.3020, 'q': 1.3314},
+    'Kr': {'omega': 0.6359, 'm': 0.2796, 'q': 1.3741},
+    'Xe': {'omega': 0.5152, 'm': 0.2541, 'q': 1.3570},
+}
+
+ENERGY_UNIT_CONVERSION_FACTOR = {
+    'hartree': 1.0,
+    'eV': 27.2107,
+    'cm-1': 219474.63,
+    'kcalPerMol': 627.503,
+    'kJPerMol': 2625.5,
+    'kelvin': 315777,
+    'J': 43.60e-19,
+    'Hz': 6.57966e15,
+}
+
+def m(
+    alpha: float,
+    C6: float,
+    C8: float
+) -> float:
+
+    return (15 * HBAR**2 * alpha**2) / (4 * C8)
+
+def q(
+    alpha: float,
+    C6: float,
+    C8: float
+) -> float:
+
[…]

### 2022-06-20 src/gui/test.py

@@ -1,0 +1,49 @@
+from turtle import width
+from PyQt5 import QtWidgets
+from PyQt5.QtWidgets import QApplication, QMainWindow
+import sys
+
+
+
+class MyWindow(QMainWindow):
+
+    def __init__(self):
+
+        super(MyWindow, self).__init__()
+
+        self.setGeometry(200, 200, 300, 300)
+        self.setWindowTitle('Quartic Potential')
+        self.initUI()
+
+    def initUI(self):
+
+        self.label = QtWidgets.QLabel(self)
+        self.label.setText("My first label!")
+        self.label.move(50, 50)
+
+        self.b1 = QtWidgets.QPushButton(self)
+        self.b1.setText("Click me")
+        self.b1.clicked.connect(self.clicked)
+
+    def clicked(self):
+
+        self.label.setText("you pressed the button")
+        self.update()
+
+    def update(self):
+
+        self.label.adjustSize()
+
+
+
+
+def window():
+
+    app = QApplication(sys.argv)
+    win = MyWindow()
+
+
+    win.show()
+    sys.exit(app.exec_())
+
+window()

### 2022-06-20 src/gui/test2.py

@@ -1,0 +1,96 @@
+# -*- coding: utf-8 -*-
+
+# Form implementation generated from reading ui file 'src/gui/test.ui'
+#
+# Created by: PyQt5 UI code generator 5.15.4
+#
+# WARNING: Any manual changes made to this file will be lost when pyuic5 is
+# run again.  Do not edit this file unless you know what you are doing.
+
+
+from PyQt5 import QtCore, QtGui, QtWidgets
+
+
+class Ui_MainWindow(object):
+    def setupUi(self, MainWindow):
+        MainWindow.setObjectName("MainWindow")
+        MainWindow.resize(800, 600)
+
+        self.centralwidget = QtWidgets.QWidget(MainWindow)
+        self.centralwidget.setObjectName("centralwidget")
+        self.label = QtWidgets.QLabel(self.centralwidget)
+        self.label.setGeometry(QtCore.QRect(170, 100, 481, 211))
+
+        font = QtGui.QFont()
+        font.setPointSize(36)
+        self.label.setFont(font)
+        self.label.setObjectName("label")
+
+        MainWindow.setCentralWidget(self.centralwidget)
+
+        self.menubar = QtWidgets.QMenuBar(MainWindow)
+        self.menubar.setGeometry(QtCore.QRect(0, 0, 800, 22))
+        self.menubar.setObjectName("menubar")
+        self.menuFile = QtWidgets.QMenu(self.menubar)
+        self.menuFile.setObjectName("menuFile")
+        self.menuEdit = QtWidgets.QMenu(self.menubar)
+        self.menuEdit.setObjectName("menuEdit")
+        MainWindow.setMenuBar(self.menubar)
+        self.statusbar = QtWidgets.QStatusBar(MainWindow)
+        self.statusbar.setObjectName("statusbar")
+        MainWindow.setStatusBar(self.statusbar)
+        self.actionNew = QtWidgets.QAction(MainWindow)
+        self.actionNew.setObjectName("actionNew")
+        self.actionSave = QtWidgets.QAction(MainWindow)
+        self.actionSave.setObjectName("actionSave")
+        self.actionCopy = QtWidgets.QAction(MainWindow)
+        self.actionCopy.setObjectName("actionCopy")
+        self.actionPaste = QtWidgets.QAction(MainWindow)
+        self.actionPaste.setObjectName("actionPaste")
+        self.menuFile.addAction(self.actionNew)
+        self.menuFile.addAction(self.actionSave)
[…]

### 2022-06-20 src/gui/test3.py

@@ -1,0 +1,58 @@
+# -*- coding: utf-8 -*-
+
+# Form implementation generated from reading ui file 'test3.ui'
+#
+# Created by: PyQt5 UI code generator 5.15.4
+#
+# WARNING: Any manual changes made to this file will be lost when pyuic5 is
+# run again.  Do not edit this file unless you know what you are doing.
+
+
+from PyQt5 import QtCore, QtGui, QtWidgets
+
+
+class Ui_MainWindow(object):
+    def setupUi(self, MainWindow):
+        MainWindow.setObjectName("MainWindow")
+        MainWindow.resize(800, 600)
+        self.centralwidget = QtWidgets.QWidget(MainWindow)
+        self.centralwidget.setObjectName("centralwidget")
+        self.photo = QtWidgets.QLabel(self.centralwidget)
+        self.photo.setGeometry(QtCore.QRect(0, 0, 791, 451))
+        self.photo.setText("")
+        self.photo.setPixmap(QtGui.QPixmap("../../paper/assets/figures/diagram-20220619.png"))
+        self.photo.setScaledContents(True)
+        self.photo.setObjectName("photo")
+        self.qdo = QtWidgets.QPushButton(self.centralwidget)
+        self.qdo.setGeometry(QtCore.QRect(0, 450, 321, 91))
+        self.qdo.setObjectName("qdo")
+        self.bullshit = QtWidgets.QPushButton(self.centralwidget)
+        self.bullshit.setGeometry(QtCore.QRect(500, 450, 291, 101))
+        self.bullshit.setObjectName("bullshit")
+        MainWindow.setCentralWidget(self.centralwidget)
+        self.menubar = QtWidgets.QMenuBar(MainWindow)
+        self.menubar.setGeometry(QtCore.QRect(0, 0, 800, 22))
+        self.menubar.setObjectName("menubar")
+        MainWindow.setMenuBar(self.menubar)
+        self.statusbar = QtWidgets.QStatusBar(MainWindow)
+        self.statusbar.setObjectName("statusbar")
+        MainWindow.setStatusBar(self.statusbar)
+
+        self.retranslateUi(MainWindow)
+        QtCore.QMetaObject.connectSlotsByName(MainWindow)
+
+    def retranslateUi(self, MainWindow):
+        _translate = QtCore.QCoreApplication.translate
+        MainWindow.setWindowTitle(_translate("MainWindow", "MainWindow"))
[…]

### 2022-06-20 src/main.py

@@ -1,45 +1,0 @@
-from argparse import ArgumentParser
-import os
-
-from src.solver import Solver
-
-def main(args) -> None:
-
-    log_dir = './results'
-    os.makedirs(log_dir, exist_ok=True)
-
-    solver = Solver(
-        m1=args.m1,
-        m2=args.m2,
-        q1=args.q1,
-        q2=args.q2,
-        omega1=args.omega1,
-        omega2=args.omega2,
-        tau=args.tau,
-        r=args.r,
-        epsilon0=args.epsilon0,
-        S0=args.S0,
-        log_dir=log_dir
-    )
-
-    solver.solve()
-
-if __name__ == '__main__':
-
-    parser = ArgumentParser()
-
-    parser.add_argument('--m1',     nargs='+', type=float, default=1.0,   help="Mass of QDO 1")
-    parser.add_argument('--m2',     nargs='+', type=float, default=1.0,   help="Mass of QDO 2")
-    parser.add_argument('--q1',     nargs='+', type=float, default=1.0,   help="Charge of QDO 1")
-    parser.add_argument('--q2',     nargs='+', type=float, default=1.0,   help="Charge of QDO 2")
-    parser.add_argument('--omega1', nargs='+', type=float, default=1.0,   help="Frequency of QDO 1")
-    parser.add_argument('--omega2', nargs='+', type=float, default=1.0,   help="Frequency of QDO 2")
-    parser.add_argument('--r',      nargs='+', type=float, default=1.0,   help="Distance between the two QDOs")
-    parser.add_argument('--tau',    nargs='+', type=float, default=1.0,   help="Strength of the external electric field")
-    parser.add_argument('--epsilon0',          type=float, default=1.0,   help="Initialization of the ground state energy")
-    parser.add_argument('--S0',                type=float, default=-10.0, help="Initialization of the fictitious variable")
-
-    args = parser.parse_args()
-
-    main(args)
-

### 2022-06-20 archived/solver.py
minor

@@ -1,0 +1,114 @@
+import itertools
+import json
+import numpy as np
+import os
+from scipy.optimize import fsolve
+from typing import Dict, List
+
+from src.expansion_coefficients.positive_coefficient import coefPlus
+from src.expansion_coefficients.negative_coefficient import coefMinus
+from src.couplings import *
+from src.utils.atomic_data import HBAR
+
+class Solver():
+
+    def __init__(
+        self,
+        m1: List[float] ,
+        m2: List[float] ,
+        q1: List[float] ,
+        q2: List[float] ,
+        omega1: List[float],
+        omega2: List[float],
+        tau: List[float],
+        r: List[float],
+        epsilon0: float = 1.0,
+        S0: float = -10.0,
+        log_dir: str = './results'
+    ) -> None:
+
+        self.m1 = m1
+        self.m2 = m2
+        self.q1 = q1
+        self.q2 = q2
+        self.omega1 = omega1
+        self.omega2 = omega2
+        self.tau = tau
+        self.r = r
+        self.x0 = [epsilon0, S0]
+        self.log_dir = log_dir
+
+        self.grid = self._prepare_grid()
+
+    def solve(self) -> List[float]:
+
+        for i in range(len(self.grid)):
+
+            alpha_ = alpha(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['tau'])
+            beta_ = beta(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['omega1'], self.grid[i]['omega2'], self.grid[i]['r'])
+            gamma_ = gamma(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['r'])
+            delta_ = delta(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['r'])
+            H = ((self.grid[i]['m1'] + self.grid[i]['m2']) / (self.grid[i]['m1'] * self.grid[i]['m2'])) * HBAR**2 / 2
+
+            x = fsolve(self.equations, self.x0, args=(alpha_, beta_, gamma_, delta_, H))
+
+            self.grid[i]['epsilon'] = x[0]
+            self.grid[i]['S'] = x[1]
+
+        self._dump_results()
+
[…]

### 2022-06-20 src/engine/main.py

@@ -1,8 +1,7 @@
 from argparse import ArgumentParser
 import os
 
-#from src.solver import Solver
-from src.engine.solver_v2 import Solver
+from src.engine.solver import Solver
 
 def main(args) -> None:
 
@@ -20,32 +19,11 @@ def main(args) -> None:
         log_dir=log_dir
     )
 
-    #solver = Solver(
-    #    m1=args.m1,
-    #    m2=args.m2,
-    #    q1=args.q1,
-    #    q2=args.q2,
-    #    omega1=args.omega1,
-    #    omega2=args.omega2,
-    #    tau=args.tau,
-    #    r=args.r,
-    #    epsilon0=args.epsilon0,
-    #    S0=args.S0,
-    #    log_dir=log_dir
-    #)
-
     solver.solve()
 
 if __name__ == '__main__':
 
     parser = ArgumentParser()
-
-    #parser.add_argument('--m1',     nargs='+', type=float, default=1.0,   help="Mass of QDO 1")
-    #parser.add_argument('--m2',     nargs='+', type=float, default=1.0,   help="Mass of QDO 2")
-    #parser.add_argument('--q1',     nargs='+', type=float, default=1.0,   help="Charge of QDO 1")
-    #parser.add_argument('--q2',     nargs='+', type=float, default=1.0,   help="Charge of QDO 2")
-    #parser.add_argument('--omega1', nargs='+', type=float, default=1.0,   help="Frequency of QDO 1")
-    #parser.add_argument('--omega2', nargs='+', type=float, default=1.0,   help="Frequency of QDO 2")
 
     parser.add_argument('--atom1',             type=str,   default='H',       help='First atom in the diatomic molecule',  choices=['H', 'Li', 'K', 'Rb', 'Cs', 'He', 'Ne', 'Ar', 'Kr', 'Xe'])
     parser.add_argument('--atom2',             type=str,   default='H',       help='second atom in the diatomic molecule', choices=['H', 'Li', 'K', 'Rb', 'Cs', 'He', 'Ne', 'Ar', 'Kr', 'Xe'])

### 2022-06-20 src/engine/solver.py

@@ -5,38 +5,42 @@ import os
 from scipy.optimize import fsolve
 from typing import Dict, List
 
-from src.expansion_coefficients.positive_coefficient import coefPlus
-from src.expansion_coefficients.negative_coefficient import coefMinus
-from src.couplings import *
-from src.utils.atomic_data import HBAR
+from src.engine.expansion_coefficients.positive_coefficient import coefPlus
+from src.engine.expansion_coefficients.negative_coefficient import coefMinus
+from src.engine.couplings import *
+from src.engine.utils.atomic_data import *
 
 class Solver():
 
     def __init__(
         self,
-        m1: List[float] ,
-        m2: List[float] ,
-        q1: List[float] ,
-        q2: List[float] ,
-        omega1: List[float],
-        omega2: List[float],
+        atom1: str,
+        atom2: str,
         tau: List[float],
         r: List[float],
         epsilon0: float = 1.0,
         S0: float = -10.0,
+        energy_unit: str = 'hartree',
         log_dir: str = './results'
     ) -> None:
 
-        self.m1 = m1
-        self.m2 = m2
-        self.q1 = q1
-        self.q2 = q2
-        self.omega1 = omega1
-        self.omega2 = omega2
+        self.atom1 = atom1
+        self.atom2 = atom2
+
+        self.m1 = ATOMIC_PARAMETERS[atom1]['m']
+        self.q1 = ATOMIC_PARAMETERS[atom1]['q']
+        self.omega1 = ATOMIC_PARAMETERS[atom1]['omega']
+        self.m2 = ATOMIC_PARAMETERS[atom2]['m']
+        self.q2 = ATOMIC_PARAMETERS[atom2]['q']
+        self.omega2 = ATOMIC_PARAMETERS[atom2]['omega']
+
         self.tau = tau
         self.r = r
         self.x0 = [epsilon0, S0]
-        self.log_dir = log_dir
+        self.energy_unit = energy_unit
+
+        self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
+        os.makedirs(self.log_dir, exist_ok=True)
 
         self.grid = self._prepare_grid()
 
@@ -44,16 +48,17 @@ class Solver():
 
         for i in range(len(self.grid)):
 
[…]

### 2022-06-20 src/engine/solver_v2.py

@@ -1,113 +1,0 @@
-import itertools
-import json
-import numpy as np
-import os
-from scipy.optimize import fsolve
-from typing import Dict, List
-
-from src.engine.expansion_coefficients.positive_coefficient import coefPlus
-from src.engine.expansion_coefficients.negative_coefficient import coefMinus
-from src.engine.couplings import *
-from src.engine.utils.atomic_data import *
-
-class Solver():
-
-    def __init__(
-        self,
-        atom1: str,
-        atom2: str,
-        tau: List[float],
-        r: List[float],
-        epsilon0: float = 1.0,
-        S0: float = -10.0,
-        energy_unit: str = 'hartree',
-        log_dir: str = './results'
-    ) -> None:
-
-        self.atom1 = atom1
-        self.atom2 = atom2
-
-        self.m1 = ATOMIC_PARAMETERS[atom1]['m']
-        self.q1 = ATOMIC_PARAMETERS[atom1]['q']
-        self.omega1 = ATOMIC_PARAMETERS[atom1]['omega']
-        self.m2 = ATOMIC_PARAMETERS[atom2]['m']
-        self.q2 = ATOMIC_PARAMETERS[atom2]['q']
-        self.omega2 = ATOMIC_PARAMETERS[atom2]['omega']
-
-        self.tau = tau
-        self.r = r
-        self.x0 = [epsilon0, S0]
-        self.energy_unit = energy_unit
-
-        self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
-        os.makedirs(self.log_dir, exist_ok=True)
-
-        self.grid = self._prepare_grid()
-
-    def solve(self) -> List[float]:
-
-        for i in range(len(self.grid)):
-
-            alpha_ = alpha(self.m1, self.m2, self.q1, self.q2, self.grid[i]['tau'])
-            beta_ = beta(self.m1, self.m2, self.q1, self.q2, self.omega1, self.omega2, self.grid[i]['r'])
-            gamma_ = gamma(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
-            delta_ = delta(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
-            H = ((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2
-
-            x = fsolve(self.equations, self.x0, args=(alpha_, beta_, gamma_, delta_, H))
-
[…]

### 2022-06-20 paper/main.tex
script to generate latex tables

@@
 \usepackage{bm}
+\usepackage{diagbox}
 \usepackage[table]{xcolor}
@@
 
+\section{Results}
+
+\begin{table}[h!]
+\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
+\begin{ruledtabular}
+\begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+        \hline
+        1.0 & 5.428021 & 1.000000 & 3.673658 \\
+        2.0 & 0.531071 & 0.210137 & 0.872826 \\
+        3.0 & 1.532129 & 0.957917 & 0.999836 \\
+        4.0 & 1.968642 & 0.999963 & 1.000023 \\
+        5.0 & 0.031075 & 1.000000 & 1.014180 \\
+        6.0 & 0.978062 & 5.375749 & 0.970292 \\
+        7.0 & 21.654276 & 0.558010 & -34.785660 \\
+        8.0 & 43.488829 & 85.452632 & -28.868817
+\end{tabular}
+\end{ruledtabular}
+\end{table}
+
+\begin{table}[h!]
+\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
+\begin{ruledtabular}
+\begin{tabular}{c|ccc}
+    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+    \hline
+    1.0 & 1.000000 & 1.000000 & 5.739538 \\
+    2.0 & 1.266281 & 1.134311 & -0.966946 \\
+    3.0 & 0.880808 & 0.147328 & -0.206244 \\
+    4.0 & 3.755382 & 0.136923 & 1.000000 \\
+    5.0 & 1.000000 & 0.999847 & 0.415453 \\
+    6.0 & 6.604936 & 1.000000 & -1.709232 \\
+    7.0 & 1.000008 & 1.000000 & 9.223832 \\
+    8.0& 198.102785 & 1.000000 & 20.246740
+\end{tabular}
+\end{ruledtabular}
+\end{table}
+
 %\begin{acknowledgments}
@@
 
-\begin{table}[b]
-\caption{\label{tab:table2} aaa}
-\begin{ruledtabular}
-\begin{tabular}{cccccccc}
- &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
- &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
-\hline
-Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
-& 0.680 & 1.870 & 3.700 \\
-Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
-& 0.450 & 1.930 & 3.760 \\
-Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
-& 0.750 & 2.170 & 3.560 \\
-Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
-& 0.900 & 2.370 & 3.720 \\
-Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
-& 0.380 & 1.730 & 2.830 \\
-Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
-& 0.760 & 2.110 & 3.120 \\
-Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
-&  1.120 & 2.620 & 3.480 \\
-Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
-& 1.330 & 2.800 & 3.590 \\
-Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
-& 1.420 & 3.030 & 3.740 \\
-In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
-& 0.960 & 2.460 & 3.780 \\
-Tl& 0.480 & 18.90 & 3.550 & & & & \\
-\end{tabular}
-\end{ruledtabular}
-\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
-\footnotetext[2]{Here's the second.}
-\footnotetext[3]{Here's the third.}
-\footnotetext[4]{Here's the fourth.}
-\footnotetext[5]{And etc.}
-\end{table}
-
 \nocite{*}

### 2022-06-20 bash_scripts/main.sh

@@ -1,7 +1,7 @@
-python src/main.py \
+python src/engine/main.py \
     --atom1 He \
     --atom2 He \
-    --r 1.0 2.0 \
-    --tau 0.0 \
+    --r 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 \
+    --tau 0.0 1.0 2.0\
     --epsilon0 1.0 \
-    --S0 -1.0
+    --S0 -10.0

### 2022-06-20 src/engine/solver.py

@@ -60,7 +60,8 @@ class Solver():
             self.grid[i]['energy_unit'] = self.energy_unit
             #self.grid[i]['S'] = x[1]
 
-        self._dump_results()
+        self._dump_json()
+        self._dump_numpy()
 
     def equations(
         self,
@@ -107,7 +108,25 @@ class Solver():
 
         return grid
 
-    def _dump_results(self) -> None:
+    def _dump_json(self) -> None:
 
         with open(os.path.join(self.log_dir, 'results.json'), 'w') as f:
             json.dump(self.grid, f, indent=4)
+
+    def _dump_numpy(self) -> None:
+        r'''Saves the output data in a txt file, nicely formatted for latex tables.
+        The first column are the various values of the distance r.
+        The first line are the various values of the external field $\tau$.
+        '''
+
+        energy_array = np.zeros(shape=(len(self.tau) * len(self.r),))
+        for i in range(len(self.grid)):
+            energy_array[i] = self.grid[i]['epsilon']
+
+        energy_array = energy_array.reshape((len(self.tau), len(self.r))).T
+        r = np.array(self.r).reshape((-1, 1))
+        tau = np.array([0] + self.tau).reshape((1, -1))
+        energy_array = np.concatenate((r, energy_array), axis=1)
+        energy_array = np.concatenate((tau, energy_array), axis=0)
+
+        np.savetxt(os.path.join(self.log_dir, "r_vs_tau_table.txt"), energy_array, delimiter=' & ', fmt='%f', newline=' \\\\\n')

### 2022-06-23 bash_scripts/main.sh
minor

@@ -1,29 +1,17 @@
-# RUN SEQUENTIALLY
-
-#for ATOM in H Li K Rb Cs He Ne Ar Kr Xe
-#do
-#    python src/engine/main.py \
-#        --atom1 $ATOM \
-#        --atom2 $ATOM \
-#        --r 1.0 2.0 5.0 10.0 20.0 \
-#        --tau 0.0 1.0 2.0 5.0 10.0, 20.0 \
-#        --energy_unit hartree
-#done
-
 # RUN IN PARALLEL ON MULTIPLE CPUS
 
-#parallel --jobs 10 --bar python src/engine/main.py \
+#parallel --bar python src/engine/main.py \
 #    --atom1 {1} \
 #    --atom2 {1} \
-#    --r 1.0 2.0 5.0 10.0 20.0 \
-#    --tau 0.0 1.0 2.0 5.0 10.0, 20.0 \
+#    --r 1.0 2.0 5.0 7.0 10.0 15.0 20.0 \
+#    --tau 0.0 2.5 5.0 \
 #    --energy_unit hartree \
 #    ::: H Li K Rb Cs He Ne Ar Kr Xe
 
 parallel --bar python src/engine/main.py \
     --atom1 {1} \
     --atom2 {1} \
-    --r 1.0 2.0 5.0 7.0 10.0 15.0 20.0 \
-    --tau 0.0 5.0 10.0 \
+    --r 1.0 2.0 3.0 4.0 5.0 6.0 7.0 \
+    --tau 0.0 1.0 2.0 \
     --energy_unit hartree \
-    ::: H Li K Rb Cs He Ne Ar Kr Xe
+    ::: H

### 2022-06-23 bash_scripts/test.sh

@@ -1,0 +1,6 @@
+python src/engine/main.py \
+    --atom1 H \
+    --atom2 H \
+    --r  6.0 \
+    --tau 1.0 \
+    --energy_unit hartree

### 2022-06-23 src/engine/solver.py

@@ -37,8 +37,8 @@ class Solver():
 
         self.tau = tau
         self.r = r
-        self.epsilon0_list = [-20.0]
-        self.S0_list = [2 * n for n in range(-10, 5)]
+        self.epsilon0_list = [n for n in range(0, 40, 2)]
+        self.S0_list = [0]
         self.energy_unit = energy_unit
 
         self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
@@ -56,9 +56,10 @@ class Solver():
             delta_ = delta(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
             H_ = ((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2
 
+            lowest_S = float('inf')
             lowest_epsilon = float('inf')
-            for pair in itertools.product(self.epsilon0_list, self.S0_list):
-
+            for pair in tqdm(itertools.product(self.epsilon0_list, self.S0_list), leave=False):
+                print(pair)
                 epsilon0 = pair[0]
                 S0 = pair[1]
                 x0 = [epsilon0, S0]
@@ -74,7 +75,9 @@ class Solver():
 
                 if epsilon < lowest_epsilon:
                     lowest_epsilon = epsilon
+                    lowest_S = S
 
+            self.grid[i]['S'] = lowest_S
             self.grid[i]['epsilon'] = lowest_epsilon
             self.grid[i]['epsilon (in {})'.format(self.energy_unit)] = self.grid[i]['epsilon'] * ENERGY_UNIT_CONVERSION_FACTOR[self.energy_unit]
 

### 2022-06-23 bash_scripts/main.sh
corrected typo coefficients

@@ -3,15 +3,15 @@
 #parallel --bar python src/engine/main.py \
 #    --atom1 {1} \
 #    --atom2 {1} \
-#    --r 1.0 2.0 5.0 7.0 10.0 15.0 20.0 \
-#    --tau 0.0 2.5 5.0 \
+#    --r 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 \
+#    --tau 0.0 0.1 0.2 \
 #    --energy_unit hartree \
 #    ::: H Li K Rb Cs He Ne Ar Kr Xe
 
 parallel --bar python src/engine/main.py \
     --atom1 {1} \
     --atom2 {1} \
-    --r 1.0 2.0 3.0 4.0 5.0 6.0 7.0 \
-    --tau 0.0 1.0 2.0 \
+    --r 1.0 5.0 10.0 50.0 100.0 \
+    --tau 0.0 \
     --energy_unit hartree \
     ::: H

### 2022-06-23 bash_scripts/test.sh

@@ -1,6 +1,6 @@
 python src/engine/main.py \
     --atom1 H \
     --atom2 H \
-    --r  6.0 \
-    --tau 1.0 \
+    --r 4.0 \
+    --tau 0.0 \
     --energy_unit hartree

### 2022-06-23 src/engine/couplings.py

@@ -18,7 +18,7 @@ def beta(
     r: float
 ) -> float:
 
-    return ((m1 * m2) / ((m1 + m2)**2)) * ((2 * q1 * q2) / (r**3)) + 0.5 * ((m1 * m2) / (m1 + m2)) * (m1 * omega2**2 + m2 * omega1**1) / (m1 + m2)
+    return ((m1 * m2) / ((m1 + m2)**2)) * ((2 * q1 * q2) / (r**3)) + 0.5 * ((m1 * m2) / (m1 + m2)) * (m1 * omega2**2 + m2 * omega1**2) / (m1 + m2)
 
 def gamma(
     m1: float,

### 2022-06-23 src/engine/solver.py

@@ -37,7 +37,9 @@ class Solver():
 
         self.tau = tau
         self.r = r
-        self.epsilon0_list = [n for n in range(0, 40, 2)]
+        #self.epsilon0_list = [n for n in range(-10, 30)]
+        #self.S0_list = [n for n in range(-20, 20)]
+        self.epsilon0_list = [-10]
         self.S0_list = [0]
         self.energy_unit = energy_unit
 
@@ -48,7 +50,7 @@ class Solver():
 
     def solve(self) -> None:
 
-        for i in tqdm(range(len(self.grid))):
+        for i in range(len(self.grid)):
 
             alpha_ = alpha(self.m1, self.m2, self.q1, self.q2, self.grid[i]['tau'])
             beta_ = beta(self.m1, self.m2, self.q1, self.q2, self.omega1, self.omega2, self.grid[i]['r'])
@@ -58,8 +60,10 @@ class Solver():
 
             lowest_S = float('inf')
             lowest_epsilon = float('inf')
-            for pair in tqdm(itertools.product(self.epsilon0_list, self.S0_list), leave=False):
-                print(pair)
+            for pair in itertools.product(self.epsilon0_list, self.S0_list):
+
+                #print(pair)
+
                 epsilon0 = pair[0]
                 S0 = pair[1]
                 x0 = [epsilon0, S0]

### 2022-06-23 paper/main.tex
minor
mathematica file added

@@
 %\tableofcontents
+
+\section*{TO DO}
+
+    \begin{itemize}
+        \item Talk about the fact that the large coefficients $c_n$ and $d_n$ are polynomials in $\epsilon$ and $S$.
+In particular, it gives us access to only a finite number of energy levels.
+In particular $c_n$ is of degree $(\lfloor n/2\rfloor, 1)$ in $(\epsilon, S)$.
+Solving for $S$ using one of the two equations and plugging back in the other, one gets a rational function of $\epsilon$.
+The number of zeros is then bounded (some roots might be complex or there could be some simplifications between numerator and denominator) by the degree of the numerator.
+    \end{itemize}
 
@@
 \begin{tabular}{c|ccc}
-        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
     \hline
@@
 \begin{tabular}{c|ccc}
-    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
     \hline

### 2022-06-24 archived/output_mathematica/minusDenominator.py
succeeded rational function approach mathematica

@@ -1,1 +1,0 @@
-"1507645899890367707813511168000*delta**37.5*H**15"

### 2022-06-24 archived/output_mathematica/minusDenominator_N15.py

@@ -1,0 +1,1 @@
+"1507645899890367707813511168000*delta**37.5*H**15"

### 2022-06-24 archived/solver.py

@@ -1,114 +1,0 @@
-import itertools
-import json
-import numpy as np
-import os
-from scipy.optimize import fsolve
-from typing import Dict, List
-
-from src.expansion_coefficients.positive_coefficient import coefPlus
-from src.expansion_coefficients.negative_coefficient import coefMinus
-from src.couplings import *
-from src.utils.atomic_data import HBAR
-
-class Solver():
-
-    def __init__(
-        self,
-        m1: List[float] ,
-        m2: List[float] ,
-        q1: List[float] ,
-        q2: List[float] ,
-        omega1: List[float],
-        omega2: List[float],
-        tau: List[float],
-        r: List[float],
-        epsilon0: float = 1.0,
-        S0: float = -10.0,
-        log_dir: str = './results'
-    ) -> None:
-
-        self.m1 = m1
-        self.m2 = m2
-        self.q1 = q1
-        self.q2 = q2
-        self.omega1 = omega1
-        self.omega2 = omega2
-        self.tau = tau
-        self.r = r
-        self.x0 = [epsilon0, S0]
-        self.log_dir = log_dir
-
-        self.grid = self._prepare_grid()
-
-    def solve(self) -> List[float]:
-
-        for i in range(len(self.grid)):
-
-            alpha_ = alpha(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['tau'])
-            beta_ = beta(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['omega1'], self.grid[i]['omega2'], self.grid[i]['r'])
-            gamma_ = gamma(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['r'])
-            delta_ = delta(self.grid[i]['m1'], self.grid[i]['m2'], self.grid[i]['q1'], self.grid[i]['q2'], self.grid[i]['r'])
-            H = ((self.grid[i]['m1'] + self.grid[i]['m2']) / (self.grid[i]['m1'] * self.grid[i]['m2'])) * HBAR**2 / 2
-
-            x = fsolve(self.equations, self.x0, args=(alpha_, beta_, gamma_, delta_, H))
-
-            self.grid[i]['epsilon'] = x[0]
-            self.grid[i]['S'] = x[1]
-
-        self._dump_results()
-
[…]

### 2022-06-24 src/engine/solver.py

@@ -3,13 +3,14 @@ import json
 import numpy as np
 import os
 from scipy.optimize import fsolve
-from tqdm import tqdm
 from typing import Dict, List
 import warnings
 warnings.filterwarnings("error")
 
 from src.engine.expansion_coefficients.N_15.positive_coefficient import coefPlus
 from src.engine.expansion_coefficients.N_15.negative_coefficient import coefMinus
+from src.engine.expansion_coefficients.N_20.rational_numerator import rational_numerator
+from src.engine.expansion_coefficients.N_20.rational_denominator import rational_denominator
 from src.engine.couplings import *
 from src.engine.utils.atomic_data import *
 

### 2022-06-24 src/engine/utils/mathematica_formatting2.py

@@ -1,0 +1,47 @@
+with open('./archived/output_mathematica/rationalNumerator.py', 'r+') as f:
+
+    s = f.read()
+    s = '\tv0 = ' + s[1:-1]
+
+    counter = 0
+    counter_variables = 1
+
+    for i in range(len(s)):
+        if counter >= 10000 and s[i]=='+':
+            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+            counter = 0
+            counter_variables += 1
+        counter += 1
+
+num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+
+with open('./src/engine/expansion_coefficients/N_20/rational_numerator.py', 'w') as f:
+
+    f.write('import numpy as np\n\ndef rational_numerator(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
+    f.write(s)
+    f.write('\n\n')
+    f.write('\treturn ' + num)
+
+with open('./archived/output_mathematica/rationalDenominator.py', 'r+') as f:
+
+    s = f.read()
+    s = '\tv0 = ' + s[1:-1]
+
+    counter = 0
+    counter_variables = 1
+
+    for i in range(len(s)):
+        if counter >= 10000 and s[i]=='+':
+            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+            counter = 0
+            counter_variables += 1
+        counter += 1
+
+num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+
+with open('./src/engine/expansion_coefficients/N_20/rational_denominator.py', 'w') as f:
+
+    f.write('import numpy as np\n\ndef rational_denominator(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
+    f.write(s)
+    f.write('\n\n')
+    f.write('\treturn ' + num)

### 2022-06-24 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_5.py
progress

@@ -1,0 +1,1 @@
+"-4556379222741073272775317143392206807575952427111873695134515200000*alpha**9*delta**92*H**20 + 41007413004669659454977854290529861268183571844006863256210636800000*alpha**8*beta*delta**92*H**20 - 164029652018678637819911417162119445072734287376027453024842547200000*alpha**7*beta**2*delta**92*H**20 + 382735854710250154913126640044945371836380003877397390391299276800000*alpha**6*beta**3*delta**92*H**20 - 574103782065375232369689960067418057754570005816096085586948915200000*alpha**5*beta**4*delta**92*H**20 + 574103782065375232369689960067418057754570005816096085586948915200000*alpha**4*beta**5*delta**92*H**20 - 382735854710250154913126640044945371836380003877397390391299276800000*alpha**3*beta**6*delta**92*H**20 + 164029652018678637819911417162119445072734287376027453024842547200000*alpha**2*beta**7*delta**92*H**20 - 41007413004669659454977854290529861268183571844006863256210636800000*alpha*beta**8*delta**92*H**20 + 4556379222741073272775317143392206807575952427111873695134515200000*beta**9*delta**92*H**20 + 20503706502334829727488927145264930634091785922003431628105318400000*alpha**8*beta*delta**91*gamma*H**20 - 164029652018678637819911417162119445072734287376027453024842547200000*alpha**7*beta**2*delta**91*gamma*H**20 + 574103782065375232369689960067418057754570005816096085586948915200000*alpha**6*beta**3*delta**91*gamma*H**20 - 1148207564130750464739379920134836115509140011632192171173897830400000*alpha**5*beta**4*delta**91*gamma*H**20 + 1435259455163438080924224900168545144386425014540240213967372288000000*alpha**4*beta**5*delta**91*gamma*H**20 - 1148207564130750464739379920134836115509140011632192171173897830400000*alpha**3*beta**6*delta**91*gamma*H**20 + 574103782065375232369689960067418057754570005816096085586948915200000*alpha**2*beta**7*delta**91*gamma*H**20 - 164029652018678637819911417162119445072734287376027453024842547200000*alpha*beta**8*delta**91*gamma*H**20 + 20503706502334829727488927145264930634091785922003431628105318400000*beta**9*delta**91*gamma*H**20 - 41007413004669659454977854290529861268183571844006863256210636800000*alpha**7*beta**2*delta**90*gamma**2*H**20 + 2870
[…]

### 2022-06-24 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_6.py

@@ -1,0 +1,1 @@
+"8411777026598904503585200880108689490909450634668074514094489600000*alpha**7*delta**93*H**20 - 58882439186192331525096406160760826436366154442676521598661427200000*alpha**6*beta*delta**93*H**20 + 176647317558576994575289218482282479309098463328029564795984281600000*alpha**5*beta**2*delta**93*H**20 - 294412195930961657625482030803804132181830772213382607993307136000000*alpha**4*beta**3*delta**93*H**20 + 294412195930961657625482030803804132181830772213382607993307136000000*alpha**3*beta**4*delta**93*H**20 - 176647317558576994575289218482282479309098463328029564795984281600000*alpha**2*beta**5*delta**93*H**20 + 58882439186192331525096406160760826436366154442676521598661427200000*alpha*beta**6*delta**93*H**20 - 8411777026598904503585200880108689490909450634668074514094489600000*beta**7*delta**93*H**20 - 29441219593096165762548203080380413218183077221338260799330713600000*alpha**6*beta*delta**92*gamma*H**20 + 176647317558576994575289218482282479309098463328029564795984281600000*alpha**5*beta**2*delta**92*gamma*H**20 - 441618293896442486438223046205706198272746158320073911989960704000000*alpha**4*beta**3*delta**92*gamma*H**20 + 588824391861923315250964061607608264363661544426765215986614272000000*alpha**3*beta**4*delta**92*gamma*H**20 - 441618293896442486438223046205706198272746158320073911989960704000000*alpha**2*beta**5*delta**92*gamma*H**20 + 176647317558576994575289218482282479309098463328029564795984281600000*alpha*beta**6*delta**92*gamma*H**20 - 29441219593096165762548203080380413218183077221338260799330713600000*beta**7*delta**92*gamma*H**20 + 44161829389644248643822304620570619827274615832007391198996070400000*alpha**5*beta**2*delta**91*gamma**2*H**20 - 220809146948221243219111523102853099136373079160036955994980352000000*alpha**4*beta**3*delta**91*gamma**2*H**20 + 441618293896442486438223046205706198272746158320073911989960704000000*alpha**3*beta**4*delta**91*gamma**2*H**20 - 441618293896442486438223046205706198272746158320073911989960704000000*alpha**2*beta**5*delta**91*gamma**2*H**20 + 220809146948221243219111523102853099136373079160036955994980352000000*alpha*beta**6*delta**91*gamma*
[…]

### 2022-06-24 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_7.py

@@ -1,0 +1,1 @@
+"-6729421621279123602868160704086951592727560507734459611275591680000*alpha**5*delta**94*H**20 + 33647108106395618014340803520434757963637802538672298056377958400000*alpha**4*beta*delta**94*H**20 - 67294216212791236028681607040869515927275605077344596112755916800000*alpha**3*beta**2*delta**94*H**20 + 67294216212791236028681607040869515927275605077344596112755916800000*alpha**2*beta**3*delta**94*H**20 - 33647108106395618014340803520434757963637802538672298056377958400000*alpha*beta**4*delta**94*H**20 + 6729421621279123602868160704086951592727560507734459611275591680000*beta**5*delta**94*H**20 + 16823554053197809007170401760217378981818901269336149028188979200000*alpha**4*beta*delta**93*gamma*H**20 - 67294216212791236028681607040869515927275605077344596112755916800000*alpha**3*beta**2*delta**93*gamma*H**20 + 100941324319186854043022410561304273890913407616016894169133875200000*alpha**2*beta**3*delta**93*gamma*H**20 - 67294216212791236028681607040869515927275605077344596112755916800000*alpha*beta**4*delta**93*gamma*H**20 + 16823554053197809007170401760217378981818901269336149028188979200000*beta**5*delta**93*gamma*H**20 - 16823554053197809007170401760217378981818901269336149028188979200000*alpha**3*beta**2*delta**92*gamma**2*H**20 + 50470662159593427021511205280652136945456703808008447084566937600000*alpha**2*beta**3*delta**92*gamma**2*H**20 - 50470662159593427021511205280652136945456703808008447084566937600000*alpha*beta**4*delta**92*gamma**2*H**20 + 16823554053197809007170401760217378981818901269336149028188979200000*beta**5*delta**92*gamma**2*H**20 - 8411777026598904503585200880108689490909450634668074514094489600000*alpha**4*delta**93*gamma**2*H**20 + 33647108106395618014340803520434757963637802538672298056377958400000*alpha**3*beta*delta**93*gamma**2*H**20 - 50470662159593427021511205280652136945456703808008447084566937600000*alpha**2*beta**2*delta**93*gamma**2*H**20 + 33647108106395618014340803520434757963637802538672298056377958400000*alpha*beta**3*delta**93*gamma**2*H**20 - 8411777026598904503585200880108689490909450634668074514094489600000*beta**4*delta**93*gamma**2*H**20 + 8411777026598904503585200
[…]

### 2022-06-24 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_8.py

@@ -1,0 +1,1 @@
+"1979241653317389294961223736496162233155164855216017532728115200000*alpha**3*delta**95*H**20 - 5937724959952167884883671209488486699465494565648052598184345600000*alpha**2*beta*delta**95*H**20 + 5937724959952167884883671209488486699465494565648052598184345600000*alpha*beta**2*delta**95*H**20 - 1979241653317389294961223736496162233155164855216017532728115200000*beta**3*delta**95*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha**2*beta*delta**94*gamma*H**20 + 5937724959952167884883671209488486699465494565648052598184345600000*alpha*beta**2*delta**94*gamma*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*beta**3*delta**94*gamma*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*alpha*beta**2*delta**93*gamma**2*H**20 - 1484431239988041971220917802372121674866373641412013149546086400000*beta**3*delta**93*gamma**2*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*alpha**2*delta**94*gamma**2*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha*beta*delta**94*gamma**2*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*beta**2*delta**94*gamma**2*H**20 - 247405206664673661870152967062020279144395606902002191591014400000*beta**3*delta**92*gamma**3*H**20 + 742215619994020985610458901186060837433186820706006574773043200000*alpha**2*delta**93*gamma**3*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha*beta*delta**93*gamma**3*H**20 + 2226646859982062956831376703558182512299560462118019724319129600000*beta**2*delta**93*gamma**3*H**20 - 742215619994020985610458901186060837433186820706006574773043200000*alpha*beta*delta**92*gamma**4*H**20 + 1113323429991031478415688351779091256149780231059009862159564800000*beta**2*delta**92*gamma**4*H**20 + 371107809997010492805229450593030418716593410353003287386521600000*alpha*delta**93*gamma**4*H**20 - 371107809997010492805229450593030418716593410353003287386521600000*beta*delta**93*gamma**4*H**20 + 185553904998505246402614725296515209358296705176501643693260800000*beta**2*delta**91*gamma**5*H**20 + 3711078099970104928052294505930304
[…]

### 2022-06-24 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_9.py

@@ -1,0 +1,1 @@
+"-138894151109992231225349034140081560221415077559018774226534400000*alpha*delta**96*H**20 + 138894151109992231225349034140081560221415077559018774226534400000*beta*delta**96*H**20 + 69447075554996115612674517070040780110707538779509387113267200000*beta*delta**95*gamma*H**20 - 34723537777498057806337258535020390055353769389754693556633600000*delta**95*gamma**2*H**20 - 17361768888749028903168629267510195027676884694877346778316800000*delta**94*gamma**3*H**20 + 5555766044399689249013961365603262408856603102360750969061376000000*delta**96.5*H**21"

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_14.py

@@ -1,0 +1,1 @@
+"1296565325842570429448886660371775737957701386240*alpha**10*beta*delta**91 - 66989208501866138854859144119208413127814571622400*alpha**8*beta**3*delta**91 + 884257552224633032884140702373551053287152345415680*alpha**6*beta**5*delta**91 - 4421287761123165164420703511867755266435761727078400*alpha**4*beta**7*delta**91 + 9088202620086506171309223885505941381006843550105600*alpha**2*beta**9*delta**91 - 6444361857879522557837449664267849342895761790074880*beta**11*delta**91 - 6482826629212852147244433301858878689788506931200*alpha**9*beta**2*delta**90*gamma + 267956834007464555419436576476833652511258286489600*alpha**7*beta**4*delta**90*gamma - 2652772656673899098652422107120653159861457036247040*alpha**5*beta**6*delta**90*gamma + 8842575522246330328841407023735510532871523454156800*alpha**3*beta**8*delta**90*gamma - 9088202620086506171309223885505941381006843550105600*alpha*beta**10*delta**90*gamma + 14586359915728917331299974929182477052024140595200*alpha**8*beta**3*delta**89*gamma**2 - 468924459513062971984014008834458891894702001356800*alpha**6*beta**5*delta**89*gamma**2 + 3315965820842373873315527633900816449826821295308800*alpha**4*beta**7*delta**89*gamma**2 - 6631931641684747746631055267801632899653642590617600*alpha**2*beta**9*delta**89*gamma**2 + 2272050655021626542827305971376485345251710887526400*beta**11*delta**89*gamma**2 - 324141331460642607362221665092943934489425346560*alpha**10*delta**90*gamma**2 + 50241906376399604141144358089406309845860928716800*alpha**8*beta**2*delta**90*gamma**2 - 1105321940280791291105175877966938816608940431769600*alpha**6*beta**4*delta**90*gamma**2 + 7737253581965539037736231145768571716262583022387200*alpha**4*beta**6*delta**90*gamma**2 - 20448455895194638885445753742388368107265397987737600*alpha**2*beta**8*delta**90*gamma**2 + 17721995109168687034052986576736585692963344922705920*beta**10*delta**90*gamma**2 - 19448479887638556441733299905576636069365520793600*alpha**7*beta**4*delta**88*gamma**3 + 468924459513062971984014008834458891894702001356800*alpha**5*beta**6*delta**88*gamma**3 - 221064388056
[…]

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_15.py

@@ -1,0 +1,1 @@
+"1728753767790093905931848880495700983943601848320*alpha**8*beta*delta**92 - 76065165782764131861001350741810843293518481326080*alpha**6*beta**3*delta**92 + 798684240719023384540514182789013854581944053923840*alpha**4*beta**5*delta**92 - 2814411133962272878857049977447001201860183809064960*alpha**2*beta**7*delta**92 + 3048945395125795618761804142234251302015199126487040*beta**9*delta**92 - 6915015071160375623727395521982803935774407393280*alpha**7*beta**2*delta**91*gamma + 228195497348292395583004052225432529880555443978240*alpha**5*beta**4*delta**91*gamma - 1597368481438046769081028365578027709163888107847680*alpha**3*beta**6*delta**91*gamma + 2814411133962272878857049977447001201860183809064960*alpha*beta**8*delta**91*gamma + 12101276374530657341522942163469906887605212938240*alpha**6*beta**3*delta**90*gamma**2 - 285244371685365494478755065281790662350694304972800*alpha**4*beta**5*delta**90*gamma**2 + 1198026361078535076810771274183520781872916080885760*alpha**2*beta**7*delta**90*gamma**2 - 703602783490568219714262494361750300465045952266240*beta**9*delta**90*gamma**2 - 432188441947523476482962220123925245985900462080*alpha**8*delta**91*gamma**2 + 57048874337073098895751013056358132470138860994560*alpha**6*beta**2*delta**91*gamma**2 - 998355300898779230675642728486267318227430067404800*alpha**4*beta**4*delta**91*gamma**2 + 4925219484433977537999837460532252103255321665863680*alpha**2*beta**6*delta**91*gamma**2 - 6860127139033040142214059320027065429534198034595840*beta**8*delta**91*gamma**2 - 12101276374530657341522942163469906887605212938240*alpha**5*beta**4*delta**89*gamma**3 + 190162914456910329652503376854527108233796203315200*alpha**3*beta**6*delta**89*gamma**3 - 399342120359511692270257091394506927290972026961920*alpha*beta**8*delta**89*gamma**3 + 3457507535580187811863697760991401967887203696640*alpha**7*beta*delta**90*gamma**3 - 228195497348292395583004052225432529880555443978240*alpha**5*beta**3*delta**90*gamma**3 + 2396052722157070153621542548367041563745832161771520*alpha**3*beta**5*delta**90*gamma**3 - 56288222679245457577140999548
[…]

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_16.py

@@ -1,0 +1,1 @@
+"1728753767790093905931848880495700983943601848320*alpha**6*beta*delta**93 - 60506381872653286707614710817349534438026064691200*alpha**4*beta**3*delta**93 + 447747225857634321636348860048386554841392878714880*alpha**2*beta**5*delta**93 - 831530562307035168753219311518432173276872489041920*beta**7*delta**93 - 5186261303370281717795546641487102951830805544960*alpha**5*beta**2*delta**92*gamma + 121012763745306573415229421634699068876052129382400*alpha**3*beta**4*delta**92*gamma - 447747225857634321636348860048386554841392878714880*alpha*beta**6*delta**92*gamma + 6482826629212852147244433301858878689788506931200*alpha**4*beta**3*delta**91*gamma**2 - 90759572808979930061422066226024301657039097036800*alpha**2*beta**5*delta**91*gamma**2 + 111936806464408580409087215012096638710348219678720*beta**7*delta**91*gamma**2 - 432188441947523476482962220123925245985900462080*alpha**6*delta**92*gamma**2 + 45379786404489965030711033113012150828519548518400*alpha**4*beta**2*delta**92*gamma**2 - 559684032322042902045436075060483193551741098393600*alpha**2*beta**4*delta**92*gamma**2 + 1455178484037311545318133795157256303234526855823360*beta**6*delta**92*gamma**2 - 4321884419475234764829622201239252459859004620800*alpha**3*beta**4*delta**90*gamma**3 + 30253190936326643353807355408674767219013032345600*alpha*beta**6*delta**90*gamma**3 + 2593130651685140858897773320743551475915402772480*alpha**5*beta*delta**91*gamma**3 - 121012763745306573415229421634699068876052129382400*alpha**3*beta**3*delta**91*gamma**3 + 671620838786451482454523290072579832262089318072320*alpha*beta**5*delta**91*gamma**3 + 1620706657303213036811108325464719672447126732800*alpha**2*beta**5*delta**89*gamma**4 - 3781648867040830419225919426084345902376629043200*beta**7*delta**89*gamma**4 - 4862119971909639110433324976394159017341380198400*alpha**4*beta**2*delta**90*gamma**4 + 113449466011224912576777582782530377071298871296000*alpha**2*beta**4*delta**90*gamma**4 - 195889411312715015715902626271169117743109384437760*beta**6*delta**90*gamma**4 - 11344946601122491257677758278253037707129887129600*a
[…]

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_17.py

@@ -1,0 +1,1 @@
+"1220296777263595698304834503879318341607248363520*alpha**4*beta*delta**94 - 30100653839168693891519251095689852426312126300160*alpha**2*beta**3*delta**94 + 117392549972757906176925079273190424462617292570624*beta**5*delta**94 - 2440593554527191396609669007758636683214496727040*alpha**3*beta**2*delta**93*gamma + 30100653839168693891519251095689852426312126300160*alpha*beta**4*delta**93*gamma + 1830445165895393547457251755818977512410872545280*alpha**2*beta**3*delta**92*gamma**2 - 7525163459792173472879812773922463106578031575040*beta**5*delta**92*gamma**2 - 305074194315898924576208625969829585401812090880*alpha**4*delta**93*gamma**2 + 22575490379376520418639438321767389319734094725120*alpha**2*beta**2*delta**93*gamma**2 - 146740687465947382721156349091488030578271615713280*beta**4*delta**93*gamma**2 - 610148388631797849152417251939659170803624181760*alpha*beta**4*delta**91*gamma**3 + 1220296777263595698304834503879318341607248363520*alpha**3*beta*delta**92*gamma**3 - 30100653839168693891519251095689852426312126300160*alpha*beta**3*delta**92*gamma**3 + 76268548578974731144052156492457396350453022720*beta**5*delta**90*gamma**4 - 1372833874421545160592938816864233134308154408960*alpha**2*beta**2*delta**91*gamma**4 + 9406454324740216841099765967403078883222539468800*beta**4*delta**91*gamma**4 - 5643872594844130104659859580441847329933523681280*alpha**2*beta*delta**92*gamma**4 + 73370343732973691360578174545744015289135807856640*beta**3*delta**92*gamma**4 + 610148388631797849152417251939659170803624181760*alpha*beta**3*delta**90*gamma**5 - 152537097157949462288104312984914792700906045440*alpha**3*delta**91*gamma**5 + 11287745189688260209319719160883694659867047362560*alpha*beta**2*delta**91*gamma**5 - 95335685723718413930065195615571745438066278400*beta**4*delta**89*gamma**6 + 343208468605386290148234704216058283577038602240*alpha**2*beta*delta**90*gamma**6 - 4703227162370108420549882983701539441611269734400*beta**3*delta**90*gamma**6 + 470322716237010842054988298370153944161126973440*alpha**2*delta**91*gamma**6 - 1834258593324342284014454363643600382228395
[…]

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_18.py

@@ -1,0 +1,1 @@
+"542354123228264754802148668390808151825443717120*alpha**2*beta*delta**95 - 7050603601967441812427932689080505973730768322560*beta**3*delta**95 - 542354123228264754802148668390808151825443717120*alpha*beta**2*delta**94*gamma + 135588530807066188700537167097702037956360929280*beta**3*delta**93*gamma**2 - 135588530807066188700537167097702037956360929280*alpha**2*delta**94*gamma**2 + 5287952701475581359320949516810379480298076241920*beta**2*delta**94*gamma**2 + 271177061614132377401074334195404075912721858560*alpha*beta*delta**93*gamma**3 - 101691398105299641525402875323276528467270696960*beta**2*delta**92*gamma**4 - 1321988175368895339830237379202594870074519060480*beta*delta**93*gamma**4 - 33897132701766547175134291774425509489090232320*alpha*delta**92*gamma**5 + 25422849526324910381350718830819132116817674240*beta*delta**91*gamma**6 + 110165681280741278319186448266882905839543255040*delta**92*gamma**6 - 2118570793860409198445893235901594343068139520*delta**90*gamma**8 + 20609456682674060682481649398850709769366861250560*alpha**2*delta**95.5*H - 846072432236093017491351922689660716847692198707200*beta**2*delta**95.5*H - 20609456682674060682481649398850709769366861250560*alpha*beta*delta**94.5*gamma*H + 1084708246456529509604297336781616303650887434240*alpha*delta**95.5*gamma*H + 5152364170668515170620412349712677442341715312640*beta**2*delta**93.5*gamma**2*H + 422493861994818243990873812676439550272020655636480*beta*delta**94.5*gamma**2*H + 5152364170668515170620412349712677442341715312640*alpha*delta**93.5*gamma**3*H - 2576182085334257585310206174856338721170857656320*beta*delta**92.5*gamma**4*H - 52743938483948747404508958001006092765024401489920*delta**93.5*gamma**4*H + 322022760666782198163775771857042340146357207040*delta**91.5*gamma**6*H - 33018519022136758272354810931632400283133013498265600*beta*delta**96*H**2 - 26032997914956708230503136082758791287621298421760*delta**97*H**2 + 8254629755534189568088702732908100070783253374566400*delta**95*gamma**2*H**2 - 418784159791936913068027115784646422513534620611379200*delta**96.5*H**3"

### 2022-06-24 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_19.py

@@ -1,0 +1,1 @@
+"114179815416476790484662877555959610910619729920*beta*delta**96 - 28544953854119197621165719388989902727654932480*delta**95*gamma**2 + 4567192616659071619386515102238384436424789196800*delta**96.5*H"

### 2022-06-24 src/engine/utils/mathematica_formatting3.py

@@ -1,0 +1,23 @@
+for i in range(20):
+
+    with open('./archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_{}.py'.format(i), 'r+') as f:
+
+        s = f.read()
+        s = '\tv0 = ' + s[1:-1]
+
+        counter = 0
+        counter_variables = 1
+
+        for i in range(len(s)):
+            if counter >= 10000 and s[i]=='+':
+                s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+                counter = 0
+                counter_variables += 1
+            counter += 1
+
+    coef = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+
+    with open('./src/engine/expansion_coefficients/N_20/rationalNumerator_coefficients_{}.py'.format(i), 'w') as f:
+
+        f.write('import numpy as np\n\ndef rational_numerator_coefficients_{}(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n'.format(i))
+        f.write('\treturn ')

### 2022-06-25 archived/old_approach/mathematica_formatting.py
finished implementation second method

@@ -1,0 +1,58 @@
+with open('./archived/output_mathematica/plusNumerator.py', 'r+') as f:
+
+    s = f.read()
+    s = '\tv0 = ' + s[1:-1]
+
+    counter = 0
+    counter_variables = 1
+
+    for i in range(len(s)):
+        if counter >= 10000 and s[i]=='+':
+            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+            counter = 0
+            counter_variables += 1
+        counter += 1
+
+num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+
+with open('./archived/output_mathematica/plusDenominator.py', 'r+') as f:
+
+    denom = f.read()
+    denom = '(' + denom[1:-1] + ')'
+
+with open('./src/engine/expansion_coefficients/N_15/positive_coefficient.py', 'w') as f:
+
+    f.write('import numpy as np\n\ndef coefPlus(\n\tepsilon: float,\n\tS: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
+    f.write(s)
+    f.write('\n\n')
+    f.write('\treturn ' + num + ' / ' + denom)
+
+with open('./archived/output_mathematica/minusNumerator.py', 'r+') as f:
+
+    s = f.read()
+    s = '\tv0 = ' + s[1:-1]
+
+    counter = 0
+    counter_variables = 1
+
+    for i in range(len(s)):
+        if counter >= 10000 and s[i]=='+':
+            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+            counter = 0
+            counter_variables += 1
+
+        counter += 1
+
+num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+
+with open('./archived/output_mathematica/minusDenominator.py', 'r+') as f:
+
+    denom = f.read()
+    denom = '(' + denom[1:-1] + ')'
+
+with open('./src/engine/expansion_coefficients/N_15/negative_coefficient.py', 'w') as f:
+
[…]

### 2022-06-25 archived/old_approach/solver.py

@@ -1,0 +1,158 @@
+import itertools
+import json
+import numpy as np
+import os
+from scipy.optimize import fsolve
+from typing import Dict, List
+import warnings
+warnings.filterwarnings("error")
+
+from src.engine.expansion_coefficients.N_15.positive_coefficient import coefPlus
+from src.engine.expansion_coefficients.N_15.negative_coefficient import coefMinus
+from src.engine.expansion_coefficients.N_20.rational_numerator import rational_numerator
+from src.engine.expansion_coefficients.N_20.rational_denominator import rational_denominator
+from src.engine.couplings import *
+from src.engine.utils.atomic_data import *
+
+class Solver():
+
+    def __init__(
+        self,
+        atom1: str,
+        atom2: str,
+        tau: List[float],
+        r: List[float],
+        energy_unit: str = 'hartree',
+        log_dir: str = './results'
+    ) -> None:
+
+        self.atom1 = atom1
+        self.atom2 = atom2
+
+        self.m1 = ATOMIC_PARAMETERS[atom1]['m']
+        self.q1 = ATOMIC_PARAMETERS[atom1]['q']
+        self.omega1 = ATOMIC_PARAMETERS[atom1]['omega']
+        self.m2 = ATOMIC_PARAMETERS[atom2]['m']
+        self.q2 = ATOMIC_PARAMETERS[atom2]['q']
+        self.omega2 = ATOMIC_PARAMETERS[atom2]['omega']
+
+        self.tau = tau
+        self.r = r
+        #self.epsilon0_list = [n for n in range(-10, 30)]
+        #self.S0_list = [n for n in range(-20, 20)]
+        self.epsilon0_list = [-10]
+        self.S0_list = [0]
+        self.energy_unit = energy_unit
+
+        self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
+        os.makedirs(self.log_dir, exist_ok=True)
+
+        self.grid = self._prepare_grid()
+
+    def solve(self) -> None:
+
+        for i in range(len(self.grid)):
+
+            alpha_ = alpha(self.m1, self.m2, self.q1, self.q2, self.grid[i]['tau'])
+            beta_ = beta(self.m1, self.m2, self.q1, self.q2, self.omega1, self.omega2, self.grid[i]['r'])
+            gamma_ = gamma(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
+            delta_ = delta(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
[…]

### 2022-06-25 bash_scripts/test.sh

@@ -1,6 +1,6 @@
 python src/engine/main.py \
     --atom1 H \
     --atom2 H \
-    --r 4.0 \
+    --r 5.0 \
     --tau 0.0 \
     --energy_unit hartree

### 2022-06-25 src/engine/expansion_coefficients/N_20/coefficients_array.py

@@ -1,0 +1,56 @@
+import numpy as np
+
+from src.engine.expansion_coefficients.N_20.numerator.rationalNumerator_coefficients import *
+from src.engine.expansion_coefficients.N_20.denominator.rationalDenominator_coefficients import *
+
+def numerator_coefficients_array(
+	alpha: float,
+	beta: float,
+	gamma: float,
+	delta: float,
+	H: float
+) -> np.ndarray:
+
+    return np.array([
+        num_coef_degree_0(alpha, beta, gamma, delta, H),
+        num_coef_degree_1(alpha, beta, gamma, delta, H),
+        num_coef_degree_2(alpha, beta, gamma, delta, H),
+        num_coef_degree_3(alpha, beta, gamma, delta, H),
+        num_coef_degree_4(alpha, beta, gamma, delta, H),
+        num_coef_degree_5(alpha, beta, gamma, delta, H),
+        num_coef_degree_6(alpha, beta, gamma, delta, H),
+        num_coef_degree_7(alpha, beta, gamma, delta, H),
+        num_coef_degree_8(alpha, beta, gamma, delta, H),
+        num_coef_degree_9(alpha, beta, gamma, delta, H),
+        num_coef_degree_10(alpha, beta, gamma, delta, H),
+        num_coef_degree_11(alpha, beta, gamma, delta, H),
+        num_coef_degree_12(alpha, beta, gamma, delta, H),
+        num_coef_degree_13(alpha, beta, gamma, delta, H),
+        num_coef_degree_14(alpha, beta, gamma, delta, H),
+        num_coef_degree_15(alpha, beta, gamma, delta, H),
+        num_coef_degree_16(alpha, beta, gamma, delta, H),
+        num_coef_degree_17(alpha, beta, gamma, delta, H),
+        num_coef_degree_18(alpha, beta, gamma, delta, H),
+        num_coef_degree_19(alpha, beta, gamma, delta, H)
+    ])
+
+def denominator_coefficients_array(
+	alpha: float,
+	beta: float,
+	gamma: float,
+	delta: float,
+	H: float
+) -> np.ndarray:
+
+    return np.array([
+        den_coef_degree_0(alpha, beta, gamma, delta, H),
+        den_coef_degree_1(alpha, beta, gamma, delta, H),
+        den_coef_degree_2(alpha, beta, gamma, delta, H),
+        den_coef_degree_3(alpha, beta, gamma, delta, H),
[…]

### 2022-06-25 src/engine/solver.py

@@ -1,16 +1,13 @@
 import itertools
 import json
 import numpy as np
+import numpy.polynomial.polynomial as poly
 import os
-from scipy.optimize import fsolve
 from typing import Dict, List
 import warnings
 warnings.filterwarnings("error")
 
-from src.engine.expansion_coefficients.N_15.positive_coefficient import coefPlus
-from src.engine.expansion_coefficients.N_15.negative_coefficient import coefMinus
-from src.engine.expansion_coefficients.N_20.rational_numerator import rational_numerator
-from src.engine.expansion_coefficients.N_20.rational_denominator import rational_denominator
+from src.engine.expansion_coefficients.N_20.coefficients_array import *
 from src.engine.couplings import *
 from src.engine.utils.atomic_data import *
 
@@ -38,10 +35,6 @@ class Solver():
 
         self.tau = tau
         self.r = r
-        #self.epsilon0_list = [n for n in range(-10, 30)]
-        #self.S0_list = [n for n in range(-20, 20)]
-        self.epsilon0_list = [-10]
-        self.S0_list = [0]
         self.energy_unit = energy_unit
 
         self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
@@ -57,69 +50,26 @@ class Solver():
             beta_ = beta(self.m1, self.m2, self.q1, self.q2, self.omega1, self.omega2, self.grid[i]['r'])
             gamma_ = gamma(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
             delta_ = delta(self.m1, self.m2, self.q1, self.q2, self.grid[i]['r'])
-            H_ = ((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2
+            H_ = np.sqrt(((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2)
 
-            lowest_S = float('inf')
-            lowest_epsilon = float('inf')
-            for pair in itertools.product(self.epsilon0_list, self.S0_list):
+            pnum = poly.Polynomial(numerator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
+            pden = poly.Polynomial(denominator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
 
-                #print(pair)
+            num_roots = poly.Polynomial.roots(pnum)
+            den_roots = poly.Polynomial.roots(pden)
 
-                epsilon0 = pair[0]
-                S0 = pair[1]
[…]

### 2022-06-25 src/engine/utils/mathematica_formatting.py

@@ -1,58 +1,70 @@
-with open('./archived/output_mathematica/plusNumerator.py', 'r+') as f:
+with open('./src/engine/expansion_coefficients/N_20/numerator/rationalNumerator_coefficients.py', 'w') as f:
 
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
+    f.write('import numpy as np\n\n')
 
-    counter = 0
-    counter_variables = 1
 
-    for i in range(len(s)):
-        if counter >= 10000 and s[i]=='+':
-            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-            counter = 0
-            counter_variables += 1
-        counter += 1
+for j in range(20):
 
-num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
+    with open('./archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_{}.py'.format(j), 'r+') as f:
 
-with open('./archived/output_mathematica/plusDenominator.py', 'r+') as f:
+        s = f.read()
+        s = '\tv0 = ' + s[1:-1]
 
-    denom = f.read()
-    denom = '(' + denom[1:-1] + ')'
+        counter = 0
+        counter_variables = 1
 
-with open('./src/engine/expansion_coefficients/N_15/positive_coefficient.py', 'w') as f:
+        for i in range(len(s)):
+            if counter >= 10000 and s[i]=='+':
+                s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
+                counter = 0
+                counter_variables += 1
+            counter += 1
 
-    f.write('import numpy as np\n\ndef coefPlus(\n\tepsilon: float,\n\tS: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
-    f.write(s)
-    f.write('\n\n')
-    f.write('\treturn ' + num + ' / ' + denom)
+    num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
 
-with open('./archived/output_mathematica/minusNumerator.py', 'r+') as f:
+    with open('./src/engine/expansion_coefficients/N_20/numerator/rationalNumerator_coefficients.py', 'a') as f:
 
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
[…]

### 2022-06-25 src/engine/utils/mathematica_formatting2.py

@@ -1,47 +1,0 @@
-with open('./archived/output_mathematica/rationalNumerator.py', 'r+') as f:
-
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
-
-    counter = 0
-    counter_variables = 1
-
-    for i in range(len(s)):
-        if counter >= 10000 and s[i]=='+':
-            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-            counter = 0
-            counter_variables += 1
-        counter += 1
-
-num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
-
-with open('./src/engine/expansion_coefficients/N_20/rational_numerator.py', 'w') as f:
-
-    f.write('import numpy as np\n\ndef rational_numerator(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
-    f.write(s)
-    f.write('\n\n')
-    f.write('\treturn ' + num)
-
-with open('./archived/output_mathematica/rationalDenominator.py', 'r+') as f:
-
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
-
-    counter = 0
-    counter_variables = 1
-
-    for i in range(len(s)):
-        if counter >= 10000 and s[i]=='+':
-            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-            counter = 0
-            counter_variables += 1
-        counter += 1
-
-num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
-
-with open('./src/engine/expansion_coefficients/N_20/rational_denominator.py', 'w') as f:
-
-    f.write('import numpy as np\n\ndef rational_denominator(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
-    f.write(s)
-    f.write('\n\n')
-    f.write('\treturn ' + num)

### 2022-06-25 src/engine/utils/mathematica_formatting3.py

@@ -1,23 +1,0 @@
-for i in range(20):
-
-    with open('./archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_{}.py'.format(i), 'r+') as f:
-
-        s = f.read()
-        s = '\tv0 = ' + s[1:-1]
-
-        counter = 0
-        counter_variables = 1
-
-        for i in range(len(s)):
-            if counter >= 10000 and s[i]=='+':
-                s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-                counter = 0
-                counter_variables += 1
-            counter += 1
-
-    coef = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
-
-    with open('./src/engine/expansion_coefficients/N_20/rationalNumerator_coefficients_{}.py'.format(i), 'w') as f:
-
-        f.write('import numpy as np\n\ndef rational_numerator_coefficients_{}(\n\tepsilon: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n'.format(i))
-        f.write('\treturn ')

### 2022-06-25 src/engine/solver.py
minor

@@ -58,17 +58,13 @@ class Solver():
             num_roots = poly.Polynomial.roots(pnum)
             den_roots = poly.Polynomial.roots(pden)
 
-            print(num_roots)
-            exit()
-
             self.grid[i]['energy_spectrum'] = num_roots.tolist()
             self.grid[i]['pole_spectrum'] = den_roots.tolist()
-            #self.grid[i]['energy_spectrum (in {})'.format(self.energy_unit)] = self.grid[i]['epsilon'] * ENERGY_UNIT_CONVERSION_FACTOR[self.energy_unit]
+            self.grid[i]['energy_spectrum (in {})'.format(self.energy_unit)] = (num_roots * ENERGY_UNIT_CONVERSION_FACTOR[self.energy_unit]).tolist()
 
             self._dump_json()
 
         #self._dump_numpy_for_latex()
-
 
 
     def _prepare_grid(self) -> List[Dict[str, float]]:

### 2022-06-25 paper/main.tex
minor

@@
 
+    \begin{figure}[h!]
+        \centering
+            \includegraphics[scale=0.33]{plus_minus_coefs}
+            \caption{\label{fig:coefs} Intersection loci of $c_{20}$ and $d_{20}$ with the $z=0$ plane}
+    \end{figure}
+
 %\begin{acknowledgments}
@@
 \appendix
+
+\section{Atomic data}
+
+    We collect here the QDO parameters obtained in \cite{PhysRevB.87.144103}.
+
+    \begin{table}[h!]
+    \caption{\label{tab:atomic_data} Parameters for QDOs (in a.u.)}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        & $\omega$ & $m$ & $q$ \\
+        \hline
+        H  & 0.4273 & 0.6099 & 0.7080 \\
+        Li & 0.0687 & 1.2545 & 0.9848 \\
+        K  & 0.0630 & 0.8101 & 0.9670 \\
+        Rb & 0.0603 & 0.7343 & 0.9274 \\
+        Cs & 0.0531 & 0.6939 & 0.8950 \\
+        He & 1.0187 & 0.5083 & 0.8532 \\
+        Ne & 1.2965 & 0.3491 & 1.2494 \\
+        Ar & 0.7272 & 0.3020 & 1.3314 \\
+        Kr & 0.6359 & 0.2796 & 1.3741 \\
+        Xe & 0.5152 & 0.2541 & 1.3570
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
 

### 2022-06-25 bash_scripts/test.sh

@@ -1,6 +1,7 @@
 python src/engine/main.py \
     --atom1 H \
     --atom2 H \
-    --r 5.0 \
-    --tau 0.0 \
-    --energy_unit hartree
+    --r 0.8 0.9 1.  1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.  2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3.  3.1 3.2 3.3 3.4 3.5 3.6 3.7 3.8 3.9 4.  4.1 4.2 4.3 4.4 4.5 4.6  \
+    --tau 0.2 \
+    --energy_unit hartree \
+    --n_eigenvalues 3

### 2022-06-25 src/engine/main.py

@@ -14,6 +14,7 @@ def main(args) -> None:
         tau=args.tau,
         r=args.r,
         energy_unit=args.energy_unit,
+        n_eigenvalues=args.n_eigenvalues,
         log_dir=log_dir
     )
 
@@ -27,7 +28,8 @@ if __name__ == '__main__':
     parser.add_argument('--atom2',             type=str,   default='H',       help='second atom in the diatomic molecule', choices=['H', 'Li', 'K', 'Rb', 'Cs', 'He', 'Ne', 'Ar', 'Kr', 'Xe'])
     parser.add_argument('--r',      nargs='+', type=float, default=1.0,       help="Distance between the two QDOs, measured in atomic units (multiple of Bohr radius)")
     parser.add_argument('--tau',    nargs='+', type=float, default=1.0,       help="Strength of the external electric field")
-    parser.add_argument('--energy_unit',       type=str,   default='hartree', help="Unit of energies", choices=['hartree', 'eV', 'cm-1', 'kcalPerMol', 'kJPerMol', 'kelvin', 'J', 'Hz'])
+    parser.add_argument('--energy_unit',       type=str,   default='hartree', help="Unit of energies",                     choices=['hartree', 'eV', 'cm-1', 'kcalPerMol', 'kJPerMol', 'kelvin', 'J', 'Hz'])
+    parser.add_argument('--n_eigenvalues',     type=int,   default=3,         help="Number of energy levels to compute",   choices=[1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20])
 
     args = parser.parse_args()
 

### 2022-06-25 src/engine/solver.py

@@ -20,6 +20,7 @@ class Solver():
         tau: List[float],
         r: List[float],
         energy_unit: str = 'hartree',
+        n_eigenvalues: int = 3,
         log_dir: str = './results'
     ) -> None:
 
@@ -36,6 +37,7 @@ class Solver():
         self.tau = tau
         self.r = r
         self.energy_unit = energy_unit
+        self.n_eigenvalues = n_eigenvalues
 
         self.log_dir = os.path.join(log_dir, self.atom1 + '-' + self.atom2)
         os.makedirs(self.log_dir, exist_ok=True)
@@ -55,14 +57,17 @@ class Solver():
             pnum = poly.Polynomial(numerator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
             pden = poly.Polynomial(denominator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
 
-            num_roots = poly.Polynomial.roots(pnum)
-            den_roots = poly.Polynomial.roots(pden)
+            num_roots = poly.Polynomial.roots(pnum)[:self.n_eigenvalues]
+            #den_roots = poly.Polynomial.roots(pden)
 
             self.grid[i]['energy_spectrum'] = num_roots.tolist()
-            self.grid[i]['pole_spectrum'] = den_roots.tolist()
-            self.grid[i]['energy_spectrum (in {})'.format(self.energy_unit)] = (num_roots * ENERGY_UNIT_CONVERSION_FACTOR[self.energy_unit]).tolist()
+            #self.grid[i]['pole_spectrum'] = den_roots.tolist()
+            #self.grid[i]['energy_spectrum (in {})'.format(self.energy_unit)] = (num_roots * ENERGY_UNIT_CONVERSION_FACTOR[self.energy_unit]).tolist()
 
-            self._dump_json()
+            try:
+                self._dump_json()
+            except TypeError:
+                print(self.grid[i])
 
         #self._dump_numpy_for_latex()
 

### 2022-06-27 paper/main.tex
progress paper simulations

--- 2022-06-20 paper/main.tex
@@
 
-\title{Ground state energy of diatomic molecules\\ in the Quantum Drude Oscillator model}
+\title{Energy spectrum of diatomic molecules\\ in the Quantum Drude Oscillator model}
 %\thanks{}
@@
             V_0(x)&=\frac{2m_1m_2}{(m_1+m_2)^2}\cdot\frac{2 x^2}{4\pi\epsilon_0r^3}\,,\\
-            V_1(x)&=-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{\text{sgn}(\vec x\cdot\hat r)|x|x^2}{4\pi\epsilon_0r^4}=\mathbin{\textcolor{teal}{-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{x^3}{4\pi\epsilon_0r^4}}}\,,\\
+            %V_1(x)&=-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{\text{sgn}(\vec x\cdot\hat r)|x|x^2}{4\pi\epsilon_0r^4}=\mathbin{\textcolor{teal}{-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{x^3}{4\pi\epsilon_0r^4}}}\,,\\
+            V_1(x)&=-\frac{3m_1m_2}{(m_1+m_2)^2}\cdot\frac{x^3}{4\pi\epsilon_0r^4}\,,\\
             V_2(x)&=\frac{2m_1m_2(2m_1^2+3m_1m_2+2m_2^2)}{(m_1+m_2)^4}\cdot\frac{x^4}{4\pi\epsilon_0r^5}\,.
@@
         \end{subequations}
-
-        \textcolor{teal}{As a comment concerning this possible sign issue: maybe one can argue that provided the external field is strong enough, we can take $x^3$.}
-
         Including the contribution of the harmonic potentials present in (\ref{eq:full_QDO_Hamiltonian}) and coupling the system to an external electric field, one finally obtain the following total one-dimensional potential:
@@
     where the potential $V$ is provided by (\ref{eq:quartic_potential}) and (\ref{eq:coupling_constants}).
+
+    Following \cite{Lay_1998}, we solve the problem separately on the positive and negative real axis, and impose that the two solutions (positive and negative) $\psi_\pm$ and their first derivative match at the origin.
+For brievety reasons, we treat explicitely the case of the positive solution, the negative case being treated by perfoming the transformation $(x, \alpha, \beta, \gamma, \delta)\rightarrow (-x, -\alpha, \beta, -\gamma, \delta)$.
+
     Performing the following change of variable:
     \begin{equation}
-        \psi(x)=\exp\left[\frac{\gamma^2-4\beta\delta}{8k\delta^{3/2}}\,x-\frac{\gamma}{4k\delta^{1/2}}\,x^2-\frac{\delta^{1/2}}{3k}\,x^3\right]\phi(x)
+        \psi_+(x)=\exp\left[\frac{\gamma^2-4\beta\delta}{8k\delta^{3/2}}\,x-\frac{\gamma}{4k\delta^{1/2}}\,x^2-\frac{\delta^{1/2}}{3k}\,x^3\right]\phi_+(x)
     \end{equation}
@@
     \begin{split}
-        &\frac{\text{d}^2\phi}{\text{d}x^2}(x)+\left[\frac{\gamma^2-4\beta\delta}{4k\delta^{3/2}}-\frac{\gamma}{k\delta^{1/2}}\,x-\frac{2\delta^{1/2}}{k}\,x^2\right]\frac{\text{d}\phi}{\text{d}x}(x)\\
-        &+\left[\frac{16 \delta ^2 \left(\beta ^2+4 \delta  \epsilon \right)-8 \beta  \gamma ^2 \delta +\gamma ^4-32 \gamma  \delta ^{5/2} k}{64 \delta ^3 k^2}-\frac{8 \alpha  \delta ^2-4 \beta  \gamma  \delta +\gamma ^3+16 \delta ^{5/2} k}{8 \delta ^2 k^2}\,x\right]\phi(x)=0\,,
+        &\frac{\text{d}^2\phi_+}{\text{d}x^2}(x)+\left[\frac{\gamma^2-4\beta\delta}{4k\delta^{3/2}}-\frac{\gamma}{k\delta^{1/2}}\,x-\frac{2\delta^{1/2}}{k}\,x^2\right]\frac{\text{d}\phi_+}{\text{d}x}(x)\\
+        &+\left[\frac{16 \delta ^2 \left(\beta ^2+4 \delta  \epsilon \right)-8 \beta  \gamma ^2 \delta +\gamma ^4-32 \gamma  \delta ^{5/2} k}{64 \delta ^3 k^2}-\frac{8 \alpha  \delta ^2-4 \beta  \gamma  \delta +\gamma ^3+16 \delta ^{5/2} k}{8 \delta ^2 k^2}\,x\right]\phi_+(x)=0\,,
     \end{split}
@@
     \begin{equation}
-        \phi(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f(x)\,,
+        \phi_+(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f_+(x)\,,
     \end{equation}
@@
     \begin{equation}
-        f(z)=\sum_{n\geq 0}c_nz^n\,.
+        f_+(z)=\sum_{n\geq 0}c^+_nz^n\,.
     \end{equation}
@@
     \begin{split}
-        &(n+1)(n+2) c_{n+2}+(n+1)(A -4n)c_{n+1} +[6(n-1) n+B n+E]c_n \\
-        &+[C (n-1)+F-4(n-2) (n-1)]c_{n-1} + [(n-3) (n-2)+D (n-2)+G]c_{n-2}=0\ \ \ (n\geq 2)
+        &(n+1)(n+2) c^+_{n+2}+(n+1)(A -4n)c^+_{n+1} +[6(n-1) n+B n+E]c^+_n \\
+        &+[C (n-1)+F-4(n-2) (n-1)]c^+_{n-1} + [(n-3) (n-2)+D (n-2)+G]c^+_{n-2}=0\ \ \ (n\geq 2)
     \end{split}
@@
     where the various coefficients are listed in full details in appendix.
-The coefficients $c_0$ and $c_1$ are to be fixed through boundary conditions, and the coeffients $c_2$ and $c_3$ are in turn fixed by the following relations
+The coefficients $c^+_0$ and $c^+_1$ are to be fixed through boundary conditions, and the coeffients $c^+_2$ and $c^+_3$ are in turn fixed by the following relations
     \begin{equation}
     \begin{split}
-        c_2&=-Ec_0-Ac_1\,,\\
-        c_3&=-\frac{ F c_0+(B+E)c_1 +2 (A-4)c_2 }{6}\,.
+        c^+_2&=-Ec^+_0-Ac^+_1\,,\\
+        c^+_3&=-\frac{ F c^+_0+(B+E)c^+_1 +2 (A-4)c^+_2 }{6}\,.
     \end{split}
     \end{equation}
+    Let us similarly denote by $c^-_n$ the coefficients in the series expansion corresponding to the solution on the negative real axis.
+It has been shown in \cite{Lay_1998} and \cite{doi:10.1063/1.531962} that the smooth matching of the two solutions at the origin can be achieved by imposing the so-called \textit{dominant solution} to the above defined difference equations vanishes.
+The conditions
+    \begin{equation}
+        \psi_+(0) = \psi_-(0)\ \ \ \text{and}\ \ \ \frac{\text{d}\psi_+}{\text{d}x}(0) = \frac{\text{d}\psi_-}{\text{d}x}(0)
+    \end{equation}
+    lead to constraints on the initial conditions for the difference equations, namely that $c^+_0 = c^-_0$ and:
+    \begin{equation}
+    \label{eq:initial_constraint}
+    \begin{split}
+        &c^+_1-c^+_0 \left[1+\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (\gamma+2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]\\
+        & = -c^-_1+c^-_0 \left[1-\frac{8 \delta ^2 (\alpha -\beta )+2 \gamma  \delta  (\gamma -2 \beta )+\gamma ^3}{16 \delta ^{5/2} k}\right]
+    \end{split}
+    \end{equation}
+    The two sides of relation (\ref{eq:initial_constraint}) are therefore equal to some quantity $s$, which parameterizes the solution.
+Now, the vanishing of the dominant solution can be achieved by imposing that the series coefficients $c^+_n(\epsilon, s)$ and $c^-_n(\epsilon, s)$ are identically $0$ asymptotically in $n$.
+This provides a pair of algebraic equations in the energy variable $\epsilon$ and the \textit{shift} variable $s$.
+
+    Let us make a few remarks at this stage.
+Imposing the vanishing of $c^\pm_n$ asymptotically in $n$ means that practically one should fix a large value of $n$, denote it $N$, and impose that the polynomials $c^\pm_N$ vanish.
+One observes that $c^-_N$ is a linear function of $s$.
+One can therefore solve explicitely for the shift variable in terms of the energy $\epsilon$.
+Plugging back into the other constraint, one obtains a rational function of the form:
+    \begin{equation}
+        c^+_N(\epsilon, s(\epsilon)) = \frac{P_N(\epsilon)}{Q_N(\epsilon)}
+    \end{equation}
+    where $P_n$ and $Q_N$ are polynomial functions of $\epsilon$, whose degree $d_N$ is an non-decreasing function of $N$.
+The $N$ zeros $\left\{\epsilon_i\right\}_{i=1}^N$ correspond then to first $N$ energy levels of the system, provided they are not complex and that $Q_N$ does not admit a zero of the same order.
 
@@
 \begin{tabular}{c|ccc}
-        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
     \hline
@@
 \begin{tabular}{c|ccc}
-    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
+    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
     \hline
@@
 
+    \begin{figure}[h!]
+        \centering
+            \includegraphics[scale=0.33]{plus_minus_coefs}
+            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$.}
+    \end{figure}
+
 %\begin{acknowledgments}

### 2022-06-27 bash_scripts/main.sh

@@ -1,17 +1,17 @@
 # RUN IN PARALLEL ON MULTIPLE CPUS
 
-#parallel --bar python src/engine/main.py \
-#    --atom1 {1} \
-#    --atom2 {1} \
-#    --r 1.0 2.0 3.0 4.0 5.0 6.0 7.0 8.0 9.0 \
-#    --tau 0.0 0.1 0.2 \
-#    --energy_unit hartree \
-#    ::: H Li K Rb Cs He Ne Ar Kr Xe
-
 parallel --bar python src/engine/main.py \
     --atom1 {1} \
     --atom2 {1} \
-    --r 1.0 5.0 10.0 50.0 100.0 \
+    --r 0.5 1.0 1.5 2.0 2.5 3.0 \
     --tau 0.0 \
     --energy_unit hartree \
-    ::: H
+    ::: H Li K Rb Cs He Ne Ar Kr Xe
+
+#parallel --bar python src/engine/main.py \
+#    --atom1 {1} \
+#    --atom2 {1} \
+#    --r 0.5 1.0 1.5 2.0 2.5 3.0 \
+#    --tau 0.0 \
+#    --energy_unit hartree \
+#    ::: H

### 2022-06-27 src/engine/solver.py

@@ -57,7 +57,7 @@ class Solver():
             pnum = poly.Polynomial(numerator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
             pden = poly.Polynomial(denominator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
 
-            num_roots = poly.Polynomial.roots(pnum)[:self.n_eigenvalues]
+            num_roots = poly.Polynomial.roots(pnum)[:self.n_eigenvalues].real
             #den_roots = poly.Polynomial.roots(pden)
 
             self.grid[i]['energy_spectrum'] = num_roots.tolist()
@@ -69,7 +69,7 @@ class Solver():
             except TypeError:
                 print(self.grid[i])
 
-        #self._dump_numpy_for_latex()
+        self._dump_numpy_for_latex_2()
 
 
     def _prepare_grid(self) -> List[Dict[str, float]]:
@@ -90,9 +90,10 @@ class Solver():
         with open(os.path.join(self.log_dir, 'results.json'), 'w') as f:
             json.dump(self.grid, f, indent=4)
 
-    def _dump_numpy_for_latex(self) -> None:
+    def _dump_numpy_for_latex_1(self) -> None:
         r'''Saves the output data in a txt file, nicely formatted for latex tables.
         The first column are the various values of the distance r.
+        The first line are the various values of the external electric field strength.
         The top left value is set to 0 and is totally irrelevant, just here for formatting reasons.
         '''
 
@@ -107,3 +108,20 @@ class Solver():
         energy_array = np.concatenate((tau, energy_array), axis=0)
 
         np.savetxt(os.path.join(self.log_dir, "r_vs_tau_table.txt"), energy_array, delimiter=' & ', fmt='%f', newline=' \\\\\n')
+
+    def _dump_numpy_for_latex_2(self) -> None:
+        r'''Saves the output data in a txt file, nicely formatted for latex tables.
+        The first column are the various values of the distance r.
+        The the variou
+        The top left value is set to 0 and is totally irrelevant, just here for formatting reasons.
+        '''
+
+        energy_array = np.zeros(shape=(len(self.r), 3))
+        for i in range(len(self.grid)):
+            for j in range(3):
+                energy_array[i][j] = self.grid[i]["energy_spectrum"][j]
+
+        r = np.array(self.r).reshape((-1, 1))
[…]

### 2022-06-27 paper/main.tex
tables added

@@
     \begin{equation}
+    \label{eq:change_variable}
         \phi_+(x)=(1+x)^{\frac{4 \beta  \gamma  \delta -\gamma ^3-8 \delta ^2 \left(\alpha +2k \delta^{1/2} \right)}{16k \delta ^{5/2}}}f_+(x)\,,
@@
     where the various coefficients are listed in full details in appendix.
+The change of variable (\ref{eq:change_variable}) is chosen precisely such that the order of the above difference equation is as small as possible.
 The coefficients $c^+_0$ and $c^+_1$ are to be fixed through boundary conditions, and the coeffients $c^+_2$ and $c^+_3$ are in turn fixed by the following relations
@@
     \begin{table}[h!]
-\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
+    \caption{\label{tab:Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
     \begin{ruledtabular}
     \begin{tabular}{c|ccc}
-    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
         \hline
-    1.0 & 5.428021 & 1.000000 & 3.673658 \\
-    2.0 & 0.531071 & 0.210137 & 0.872826 \\
-    3.0 & 1.532129 & 0.957917 & 0.999836 \\
-    4.0 & 1.968642 & 0.999963 & 1.000023 \\
-    5.0 & 0.031075 & 1.000000 & 1.014180 \\
-    6.0 & 0.978062 & 5.375749 & 0.970292 \\
-    7.0 & 21.654276 & 0.558010 & -34.785660 \\
-    8.0 & 43.488829 & 85.452632 & -28.868817
+        0.5 & 9.247342 & 32.416619 & 62.971511 \\
+        1.0 & 2.981229 & 10.350087 & 20.248422 \\
+        1.5 & 1.563464 & 5.442288 & 10.069702 \\
+        2.0 & 1.023301 & 3.394336 & 6.337199 \\
+        2.5 & 0.748161 & 2.413177 & 4.876881 \\
+        3.0 & 0.590991 & 1.960271 & 4.289340 \\  
     \end{tabular}
@@
     \begin{table}[h!]
-\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
+    \caption{\label{tab:Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
     \begin{ruledtabular}
     \begin{tabular}{c|ccc}
-    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0\\
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
         \hline
-    1.0 & 1.000000 & 1.000000 & 5.739538 \\
-    2.0 & 1.266281 & 1.134311 & -0.966946 \\
-    3.0 & 0.880808 & 0.147328 & -0.206244 \\
-    4.0 & 3.755382 & 0.136923 & 1.000000 \\
-    5.0 & 1.000000 & 0.999847 & 0.415453 \\
-    6.0 & 6.604936 & 1.000000 & -1.709232 \\
-    7.0 & 1.000008 & 1.000000 & 9.223832 \\
-    8.0& 198.102785 & 1.000000 & 20.246740
+        0.5 & 4.076335 & 14.287104 & 27.755741 \\
+        1.0 & 1.307214 & 4.543529 & 8.897871 \\
+        1.5 & 0.673427 & 2.362932 & 4.396492 \\
+        2.0 & 0.426306 & 1.441411 & 2.686432 \\
+        2.5 & 0.296956 & 0.971662 & 1.957474 \\
+        3.0 & 0.217699 & 0.719613 & 1.585340 \\    
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:H-H} Energy spectrum (in Ha) of the H-H system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 3.757546 & 13.234211 & 25.693826 \\
+        1.0 & 1.213930 & 4.243743 & 8.293979 \\
+        1.5 & 0.649664 & 2.239448 & 4.116225 \\
+        2.0 & 0.436524 & 1.423565 & 2.744604 \\
+        2.5 & 0.330635 & 1.081656 & 2.284054 \\
+        3.0 & 0.279296 & 0.965099 & 2.204208 \\      
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:He-He} Energy spectrum (in Ha) of the He-He system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 4.838555 & 16.998352 & 32.990230 \\
+        1.0 & 1.609674 & 5.563162 & 10.796479 \\
+        1.5 & 0.928052 & 3.096340 & 5.617631 \\
+        2.0 & 0.690066 & 2.190579 & 4.209331 \\
+        2.5 & 0.597424 & 1.987363 & 4.173586 \\
+        3.0 & 0.607965 & 2.159394 & 4.851867 \\       
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:K-K} Energy spectrum (in Ha) of the K-K system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 3.900846 & 13.629450 & 26.449767 \\
+        1.0 & 1.254074 & 4.338725 & 8.463017 \\
+        1.5 & 0.646062 & 2.260433 & 4.233126 \\
+        2.0 & 0.409452 & 1.389547 & 2.556108 \\
+        2.5 & 0.286775 & 0.935829 & 1.841376 \\
+        3.0 & 0.211508 & 0.689674 & 1.476942 \\         
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 9.936548 & 34.839598 & 67.682787 \\
+        1.0 & 3.196890 & 11.107797 & 21.743625 \\
+        1.5 & 1.666467 & 5.817323 & 10.779216 \\
+        2.0 & 1.078692 & 3.598874 & 6.723190 \\
+        2.5 & 0.776461 & 2.514230 & 5.085759 \\
+        3.0 & 0.599348 & 1.984794 & 4.360291 \\           
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Li-Li} Energy spectrum (in Ha) of the Li-Li system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 2.989579 & 10.393189 & 20.094511 \\
+        1.0 & 0.965106 & 3.317199 & 6.411919 \\
+        1.5 & 0.498061 & 1.728672 & 3.276409 \\
+        2.0 & 0.316132 & 1.076633 & 1.951989 \\
+        2.5 & 0.223280 & 0.727240 & 1.384589 \\
+        3.0 & 0.166518 & 0.533844 & 1.098635 \\              
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 8.067324 & 28.257747 & 54.866835 \\
+        1.0 & 2.648128 & 9.141505 & 17.802546 \\
+        1.5 & 1.463214 & 4.975572 & 9.086247 \\
+        2.0 & 1.037985 & 3.321372 & 6.216936 \\
+        2.5 & 0.839105 & 2.707087 & 5.494303 \\
+        3.0 & 0.769833 & 2.636825 & 5.742950 \\             
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 4.031874 & 14.113400 & 27.409612 \\
+        1.0 & 1.294297 & 4.489885 & 8.780383 \\
+        1.5 & 0.666759 & 2.337266 & 4.359340 \\
+        2.0 & 0.422361 & 1.430245 & 2.650383 \\
+        2.5 & 0.294937 & 0.963709 & 1.922279 \\
+        3.0 & 0.216807 & 0.712417 & 1.550805 \\                
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
+        \hline
+        0.5 & 10.472412 & 36.762340 & 71.427248 \\
+        1.0 & 3.360994 & 11.705550 & 22.941485 \\
+        1.5 & 1.743863 & 6.103626 & 11.305873 \\
+        2.0 & 1.117696 & 3.742926 & 7.034869 \\
+        2.5 & 0.792188 & 2.580753 & 5.270133 \\
+        3.0 & 0.598300 & 1.992258 & 4.438638 \\                 
     \end{tabular}
@@
             \includegraphics[scale=0.33]{plus_minus_coefs}
-            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$.}
+            \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$.
+The purple dots correspond to the first excited states of the H-H system for $r=4$ and $\mathcal E=0$.}
     \end{figure}
@@
     \begin{split}
-        &A=-\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (2 \beta +\gamma )+\gamma ^3+32 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
-        &B=\frac{8 \delta ^2 (3 \alpha +2 \beta -\gamma )-4 \gamma  \delta  (3 \beta +\gamma )+3 \gamma ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
-        &C=-\frac{8 \delta ^2 (3 \alpha +\beta -\gamma )-2 \gamma  \delta  (6 \beta +\gamma )+3 \gamma ^3+16 \delta ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
-        &D=\frac{-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)}{8 \delta ^{5/2} k}\\
-        &E=\frac{4 \gamma ^2 \delta ^2 \left(\gamma  (4 \alpha +\gamma )+4 \beta ^2+8 \beta  \gamma \right)-32 \gamma  \delta ^3 (\alpha +\beta ) (2 \beta +\gamma )+64 \delta ^4 (\alpha +\beta )^2-4 \gamma ^4 \delta  (2 \beta +\gamma )+\gamma ^6+256 \delta ^5 \left(2 k^2+\epsilon \right)+128 \delta ^{9/2} k (3 \alpha +2 \beta -\gamma )-64 \gamma  \delta ^{7/2} k (3 \beta +\gamma )+48 \gamma ^3 \delta ^{5/2} k}{256 \delta ^5 k^2}\\
-        &F=-\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \gamma  \delta  (\beta +2 \delta )+\gamma ^3-2 \gamma ^2 \delta +8 \delta ^2 \left(\alpha +\beta +2 \delta +4 \sqrt{\delta } k\right)\right)}{128 \delta ^5 k^2}\\
-        &G=\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)\right)}{256 \delta ^5 k^2}
+        A&=-\frac{8 \delta ^2 (\alpha +\beta )-2 \gamma  \delta  (2 \beta +\gamma )+\gamma ^3+32 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
+        B&= \frac{8 \delta ^2 (3 \alpha +2 \beta -\gamma )-4 \gamma  \delta  (3 \beta +\gamma )+3 \gamma ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
+        C&= -\frac{8 \delta ^2 (3 \alpha +\beta -\gamma )-2 \gamma  \delta  (6 \beta +\gamma )+3 \gamma ^3+16 \delta ^3+96 \delta ^{5/2} k}{8 \delta ^{5/2} k}\\
+        D&= \frac{-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)}{8 \delta ^{5/2} k}\\
+        E&= \frac{4 \gamma ^2 \delta ^2 \left(\gamma  (4 \alpha +\gamma )+4 \beta ^2+8 \beta  \gamma \right)-32 \gamma  \delta ^3 (\alpha +\beta ) (2 \beta +\gamma )+64 \delta ^4 (\alpha +\beta )^2-4 \gamma ^4 \delta  (2 \beta +\gamma )}{256 \delta ^5 k^2}\\
+       &\ \ \ \ \ \  +\frac{\gamma ^6+256 \delta ^5 \left(2 k^2+\epsilon \right)+128 \delta ^{9/2} k (3 \alpha +2 \beta -\gamma )-64 \gamma  \delta ^{7/2} k (3 \beta +\gamma )+48 \gamma ^3 \delta ^{5/2} k}{256 \delta ^5 k^2}\\
+        F&= -\frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \gamma  \delta  (\beta +2 \delta )+\gamma ^3-2 \gamma ^2 \delta +8 \delta ^2 \left(\alpha +\beta +2 \delta +4 \sqrt{\delta } k\right)\right)}{128 \delta ^5 k^2}\\
+        G&= \frac{\left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +2 \sqrt{\delta } k\right)\right) \left(-4 \beta  \gamma  \delta +\gamma ^3+8 \delta ^2 \left(\alpha +4 \sqrt{\delta } k\right)\right)}{256 \delta ^5 k^2}
     \end{split}

### 2022-06-27 bash_scripts/test.sh

@@ -1,7 +1,7 @@
 python src/engine/main.py \
     --atom1 H \
     --atom2 H \
-    --r 0.8 0.9 1.  1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2.  2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3.  3.1 3.2 3.3 3.4 3.5 3.6 3.7 3.8 3.9 4.  4.1 4.2 4.3 4.4 4.5 4.6  \
+    --r 0.8 0.9 1. 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2. 2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3. 3.1 3.2 3.3 3.4 3.5 3.6 3.7 3.8 3.9 4. 4.1 4.2 4.3 4.4 4.5 4.6  \
     --tau 0.2 \
     --energy_unit hartree \
     --n_eigenvalues 3

### 2022-07-03 paper/main.tex
minor
Added numerical results to paper and plots

@@
 
-\preprint{APS/123-QED}
+%\preprint{APS/123-QED}
 
@@
 \begin{abstract}
-Abstract
-%\begin{description}
-%\item[Usage]
-%Secondary publications and information retrieval purposes.
-%\item[Structure]
-%You may use the \texttt{description} environment to structure your abstract;
-%use the optional argument of the \verb+\item+ command to give the category of each item.
-%\end{description}
+
+    We compute the energy spectrum of a system consiting of a pair of Quantum Drude Oscillators coupled through the Coulomb interaction up to Quadrupole-Quadrupole and Dipole-Octupole order in the multipolar expansion by re-expressing the Schr\"odinger equation in terms of a tri-confluent Heun equation.
+
 \end{abstract}
@@
 
+\subsection{First few energy levels}
+
     \begin{table}[h!]
-    \caption{\label{tab:Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
+    \caption{\label{tab:external_field_Ar-Ar} Energy spectrum (in Ha) of the Ar-Ar system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 9.247342 & 32.416619 & 62.971511 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
+    \caption{\label{tab:external_field_Cs-Cs} Energy spectrum (in Ha) of the Cs-Cs system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 4.076335 & 14.287104 & 27.755741 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:H-H} Energy spectrum (in Ha) of the H-H system}
+    \caption{\label{tab:external_field_H-H} Energy spectrum (in Ha) of the H-H system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 3.757546 & 13.234211 & 25.693826 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:He-He} Energy spectrum (in Ha) of the He-He system}
+    \caption{\label{tab:external_field_He-He} Energy spectrum (in Ha) of the He-He system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 4.838555 & 16.998352 & 32.990230 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:K-K} Energy spectrum (in Ha) of the K-K system}
+    \caption{\label{tab:external_field_K-K} Energy spectrum (in Ha) of the K-K system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 3.900846 & 13.629450 & 26.449767 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
+    \caption{\label{tab:external_field_Kr-Kr} Energy spectrum (in Ha) of the Kr-Kr system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 9.936548 & 34.839598 & 67.682787 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Li-Li} Energy spectrum (in Ha) of the Li-Li system}
+    \caption{\label{tab:external_field_Li-Li} Energy spectrum (in Ha) of the Li-Li system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 2.989579 & 10.393189 & 20.094511 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
+    \caption{\label{tab:external_field_Ne-Ne} Energy spectrum (in Ha) of the Ne-Ne system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 8.067324 & 28.257747 & 54.866835 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
+    \caption{\label{tab:external_field_Rb-Rb} Energy spectrum (in Ha) of the Rb-Rb system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 4.031874 & 14.113400 & 27.409612 \\
@@
     \begin{table}[h!]
-    \caption{\label{tab:Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
+    \caption{\label{tab:external_field_Xe-Xe} Energy spectrum (in Ha) of the Xe-Xe system}
     \begin{ruledtabular}
@@
         \diagbox[height=1.8\line]{$r$ (a.u.)}{spectrum}& $\epsilon_0$ & $\epsilon_1$ & $\epsilon_2$ \\
-        \hline
+        \hline\\[-0.8em]
         0.5 & 10.472412 & 36.762340 & 71.427248 \\
@@
 
+\subsection{Ground state energy $r$ vs. $\mathcal E$}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Ar-Ar} Ground state energy (in Ha) of the Ar-Ar system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 9.247342 & 9.110717 & 8.952432 \\
+        1.0 & 2.981229 & 2.633184 & 2.076356 \\
+        1.5 & 1.563464 & 0.829677 & -0.591543 \\
+        2.0 & 1.023301 & -0.325559 & -2.992697 \\
+        2.5 & 0.748161 & -1.377726 & -5.452778 \\
+        3.0 & 0.590991 & -2.381467 & -7.976320 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Cs-Cs} Ground state energy (in Ha) of the Cs-Cs system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 4.076335 & 3.980857 & 3.863462 \\
+        1.0 & 1.307214 & 1.035551 & 0.558141 \\
+        1.5 & 0.673427 & 0.042066 & -1.194431 \\
+        2.0 & 0.426306 & -0.786686 & -3.026094 \\
+        2.5 & 0.296956 & -1.655817 & -5.032131 \\
+        3.0 & 0.217699 & -2.584558 & -7.136808 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:H-H} Ground state energy (in Ha) of the H-H system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 3.757546 & 3.680220 & 3.584748 \\
+        1.0 & 1.213930 & 0.994879 & 0.606484 \\
+        1.5 & 0.649664 & 0.155212 & -0.841764 \\
+        2.0 & 0.436524 & -0.467646 & -2.247426 \\
+        2.5 & 0.330635 & -1.037533 & -3.672527 \\
+        3.0 & 0.279296 & -1.563088 & -5.125057 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:He-He} Ground state energy (in Ha) of the He-He system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 4.838555 & 4.747673 & 4.637588 \\
+        1.0 & 1.609674 & 1.370517 & 0.955271 \\
+        1.5 & 0.928052 & 0.449201 & -0.551122 \\
+        2.0 & 0.690066 & -0.067148 & -1.750946 \\
+        2.5 & 0.597424 & -0.386765 & -2.715690 \\
+        3.0 & 0.607965 & -0.544976 & -3.452658 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:K-K} Ground state energy (in Ha) of the K-K system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 3.900846 & 3.798718 & 3.672463 \\
+        1.0 & 1.254074 & 0.961731 & 0.444593 \\
+        1.5 & 0.646062 & -0.035078 & -1.362536 \\
+        2.0 & 0.409452 & -0.892356 & -3.275553 \\
+        2.5 & 0.286775 & -1.798818 & -5.377141 \\
+        3.0 & 0.211508 & -2.769875 & -7.827196 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Kr-Kr} Ground state energy (in Ha) of the Kr-Kr system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 9.936548 & 9.795814 & 9.633507 \\
+        1.0 & 3.196890 & 2.840242 & 2.274883 \\
+        1.5 & 1.666467 & 0.914564 & -0.532113 \\
+        2.0 & 1.078692 & -0.316154 & -3.056110 \\
+        2.5 & 0.776461 & -1.455630 & -5.674813 \\
+        3.0 & 0.599348 & -2.572968 & -8.404424 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Li-Li} Ground state energy (in Ha) of the Li-Li system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 2.989579 & 2.886101 & 2.754734 \\
+        1.0 & 0.965106 & 0.657280 & 0.096843 \\
+        1.5 & 0.498061 & -0.231815 & -1.636857 \\
+        2.0 & 0.316132 & -1.061981 & -3.526222 \\
+        2.5 & 0.223280 & -1.953835 & -5.616848 \\
+        3.0 & 0.166518 & -2.914737 & -11.972520 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Ne-Ne} Ground state energy (in Ha) of the Ne-Ne system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 8.067324 & 7.938880 & 7.788706 \\
+        1.0 & 2.648128 & 2.324114 & 1.795116 \\
+        1.5 & 1.463214 & 0.814542 & -0.481886 \\
+        2.0 & 1.037985 & -0.043649 & -2.342096 \\
+        2.5 & 0.839105 & -0.668123 & -3.988911 \\
+        3.0 & 0.769833 & -1.095276 & -5.406152 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Rb-Rb} Ground state energy (in Ha) of the Rb-Rb system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 4.031874 & 3.933375 & 3.812070 \\
+        1.0 & 1.294297 & 1.013631 & 0.519442 \\
+        1.5 & 0.666759 & 0.014231 & -1.261255 \\
+        2.0 & 0.422361 & -0.828604 & -3.131122 \\
+        2.5 & 0.294937 & -1.715198 & -5.181182 \\
+        3.0 & 0.216807 & -2.663303 & -7.510481 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
+    \begin{table}[h!]
+    \caption{\label{tab:Xe-Xe} Ground state energy (in Ha) of the Xe-Xe system}
+    \begin{ruledtabular}
+    \begin{tabular}{c|ccc}
+        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\mathcal E$ (a.u.)}& 0.0 & 1.0 & 2.0 \\
+        \hline\\[-0.8em]
+        0.5 & 10.472412 & 10.333027 & 10.172863 \\
+        1.0 & 3.360994 & 3.008892 & 2.455036 \\
+        1.5 & 1.743863 & 1.001161 & -0.421036 \\
+        2.0 & 1.117696 & -0.272030 & -2.991068 \\
+        2.5 & 0.792188 & -1.461408 & -5.680509 \\
+        3.0 & 0.598300 & -2.651579 & -8.519189 \\
+    \end{tabular}
+    \end{ruledtabular}
+    \end{table}
+
     \begin{figure}[h!]
         \centering
-            \includegraphics[scale=0.33]{plus_minus_coefs}
+            \includegraphics[scale=0.33]{plus_minus_coefs_tau0_r2_HH}
             \caption{\label{fig:coefs} Intersection loci of the three surfaces $z=c^+_{20}(\epsilon, s)$ and $z=c^-_{20}(\epsilon, s)$ and $z=0$.
-The purple dots correspond to the first excited states of the H-H system for $r=4$ and $\mathcal E=0$.}
+The purple dots correspond to the first 5 excited states of the H-H system for $r=2$ and $\mathcal E=0$.}
+    \end{figure}
+
+    \begin{figure}[h!]
+        \centering
+            \includegraphics[scale=0.33]{rational_tau0_r2_HH}
+            \caption{\label{fig:rational} Plot of  $z=c^+_{20}(\epsilon, s(\epsilon))$ for the H-H system at $r=2$ and $\mathcal E=0$.
+The zeros are denoted by purple dots and correspond to the first excited states of the system.}
     \end{figure}

### 2022-07-03 bash_scripts/main.sh

@@ -4,8 +4,9 @@ parallel --bar python src/engine/main.py \
     --atom1 {1} \
     --atom2 {1} \
     --r 0.5 1.0 1.5 2.0 2.5 3.0 \
-    --tau 0.0 \
+    --tau 0.0 1.0 2.0 \
     --energy_unit hartree \
+    --n_eigenvalues 1 \
     ::: H Li K Rb Cs He Ne Ar Kr Xe
 
 #parallel --bar python src/engine/main.py \

### 2022-07-03 src/engine/solver.py

@@ -55,7 +55,7 @@ class Solver():
             H_ = np.sqrt(((self.m1 + self.m2) / (self.m1 * self.m2)) * HBAR**2 / 2)
 
             pnum = poly.Polynomial(numerator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
-            pden = poly.Polynomial(denominator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
+            #pden = poly.Polynomial(denominator_coefficients_array(alpha_, beta_, gamma_, delta_, H_))
 
             num_roots = poly.Polynomial.roots(pnum)[:self.n_eigenvalues].real
             #den_roots = poly.Polynomial.roots(pden)
@@ -69,7 +69,8 @@ class Solver():
             except TypeError:
                 print(self.grid[i])
 
-        self._dump_numpy_for_latex_2()
+        self._dump_numpy_for_latex_1()
+        #self._dump_numpy_for_latex_2()
 
 
     def _prepare_grid(self) -> List[Dict[str, float]]:
@@ -99,7 +100,7 @@ class Solver():
 
         energy_array = np.zeros(shape=(len(self.tau) * len(self.r),))
         for i in range(len(self.grid)):
-            energy_array[i] = self.grid[i]['epsilon']
+            energy_array[i] = self.grid[i]['energy_spectrum'][0]
 
         energy_array = energy_array.reshape((len(self.tau), len(self.r))).T
         r = np.array(self.r).reshape((-1, 1))

### 2022-07-05 paper/main.tex
paper

@@
 
-    A Quantum Drude Oscillator (QDO) is a very simple atomistic model in which the properties of an atom are encompassed in a small number of parameters.
+    MBD, non-covalent interaction, linear response,
+
+    A Quantum Drude Oscillator (QDO) is a minimalistic atomistic model in which the properties of an atom are encompassed in a small number of parameters.
 The model consists in assimilating the atom to a point particle of mass $m$ and electric charge $-q$ attached to a fixed (infinite mass) center of charge $+q$ by a harmonic spring characterized by a frequency $\omega$.
-Molecules are then defined as a collections of QDOs interactig through Coulomb interactions.
+Molecules are then defined as a collections of QDOs interacting through Coulomb interactions.
 
@@
 
-    By truncating the multipolar expansion up to Dipole-Dipole, one obtain a quadratic Hamiltonian, hence the quantum Hamiltonian can be analytically diagonalized.
-Though simple, this system was shown to capture long-range phenomena in large atomistic systems \cite{https://doi.org/10.48550/arxiv.2205.11549}.
+    By truncating the multipolar expansion up to Dipole-Dipole, one obtains a quadratic Hamiltonian.
+In the case of a closed linear chain, one can analytically solve for the spectrum of the Hamiltonion \cite{doi:10.1063/1.1743992}.
+In the case of a general geometry, one can solve for the London-van der Waals interaction energy can be calculated through a perturbative approach \cite{doi:10.1063/1.1743991}.
+Though simple, this system was shown to capture long-range phenomena in large biomolecular systems \cite{https://doi.org/10.48550/arxiv.2205.11549}.
 

### 2022-07-05 archived/old_approach/mathematica_formatting.py
Delete archived directory

@@ -1,58 +1,0 @@
-with open('./archived/output_mathematica/plusNumerator.py', 'r+') as f:
-
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
-
-    counter = 0
-    counter_variables = 1
-
-    for i in range(len(s)):
-        if counter >= 10000 and s[i]=='+':
-            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-            counter = 0
-            counter_variables += 1
-        counter += 1
-
-num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
-
-with open('./archived/output_mathematica/plusDenominator.py', 'r+') as f:
-
-    denom = f.read()
-    denom = '(' + denom[1:-1] + ')'
-
-with open('./src/engine/expansion_coefficients/N_15/positive_coefficient.py', 'w') as f:
-
-    f.write('import numpy as np\n\ndef coefPlus(\n\tepsilon: float,\n\tS: float,\n\talpha: float,\n\tbeta: float,\n\tgamma: float,\n\tdelta: float,\n\tH: float\n) -> float:\n\n')
-    f.write(s)
-    f.write('\n\n')
-    f.write('\treturn ' + num + ' / ' + denom)
-
-with open('./archived/output_mathematica/minusNumerator.py', 'r+') as f:
-
-    s = f.read()
-    s = '\tv0 = ' + s[1:-1]
-
-    counter = 0
-    counter_variables = 1
-
-    for i in range(len(s)):
-        if counter >= 10000 and s[i]=='+':
-            s = s[:i] + '\n\tv' + str(counter_variables) + ' = ' + s[i+1:]
-            counter = 0
-            counter_variables += 1
-
-        counter += 1
-
-num = '(' + ''.join(['v' + str(i) + ' + ' for i in range(counter_variables)])[:-3] + ')'
-
-with open('./archived/output_mathematica/minusDenominator.py', 'r+') as f:
-
-    denom = f.read()
-    denom = '(' + denom[1:-1] + ')'
-
-with open('./src/engine/expansion_coefficients/N_15/negative_coefficient.py', 'w') as f:
-
[…]

### 2022-07-05 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_8.py

@@ -1,1 +1,0 @@
-"1979241653317389294961223736496162233155164855216017532728115200000*alpha**3*delta**95*H**20 - 5937724959952167884883671209488486699465494565648052598184345600000*alpha**2*beta*delta**95*H**20 + 5937724959952167884883671209488486699465494565648052598184345600000*alpha*beta**2*delta**95*H**20 - 1979241653317389294961223736496162233155164855216017532728115200000*beta**3*delta**95*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha**2*beta*delta**94*gamma*H**20 + 5937724959952167884883671209488486699465494565648052598184345600000*alpha*beta**2*delta**94*gamma*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*beta**3*delta**94*gamma*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*alpha*beta**2*delta**93*gamma**2*H**20 - 1484431239988041971220917802372121674866373641412013149546086400000*beta**3*delta**93*gamma**2*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*alpha**2*delta**94*gamma**2*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha*beta*delta**94*gamma**2*H**20 + 1484431239988041971220917802372121674866373641412013149546086400000*beta**2*delta**94*gamma**2*H**20 - 247405206664673661870152967062020279144395606902002191591014400000*beta**3*delta**92*gamma**3*H**20 + 742215619994020985610458901186060837433186820706006574773043200000*alpha**2*delta**93*gamma**3*H**20 - 2968862479976083942441835604744243349732747282824026299092172800000*alpha*beta*delta**93*gamma**3*H**20 + 2226646859982062956831376703558182512299560462118019724319129600000*beta**2*delta**93*gamma**3*H**20 - 742215619994020985610458901186060837433186820706006574773043200000*alpha*beta*delta**92*gamma**4*H**20 + 1113323429991031478415688351779091256149780231059009862159564800000*beta**2*delta**92*gamma**4*H**20 + 371107809997010492805229450593030418716593410353003287386521600000*alpha*delta**93*gamma**4*H**20 - 371107809997010492805229450593030418716593410353003287386521600000*beta*delta**93*gamma**4*H**20 + 185553904998505246402614725296515209358296705176501643693260800000*beta**2*delta**91*gamma**5*H**20 + 3711078099970104928052294505930304
[…]

### 2022-07-05 archived/output_mathematica_coefficients/denominator/rationalDenominator_coefficients_9.py

@@ -1,1 +1,0 @@
-"-138894151109992231225349034140081560221415077559018774226534400000*alpha*delta**96*H**20 + 138894151109992231225349034140081560221415077559018774226534400000*beta*delta**96*H**20 + 69447075554996115612674517070040780110707538779509387113267200000*beta*delta**95*gamma*H**20 - 34723537777498057806337258535020390055353769389754693556633600000*delta**95*gamma**2*H**20 - 17361768888749028903168629267510195027676884694877346778316800000*delta**94*gamma**3*H**20 + 5555766044399689249013961365603262408856603102360750969061376000000*delta**96.5*H**21"

### 2022-07-05 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_15.py

@@ -1,1 +1,0 @@
-"1728753767790093905931848880495700983943601848320*alpha**8*beta*delta**92 - 76065165782764131861001350741810843293518481326080*alpha**6*beta**3*delta**92 + 798684240719023384540514182789013854581944053923840*alpha**4*beta**5*delta**92 - 2814411133962272878857049977447001201860183809064960*alpha**2*beta**7*delta**92 + 3048945395125795618761804142234251302015199126487040*beta**9*delta**92 - 6915015071160375623727395521982803935774407393280*alpha**7*beta**2*delta**91*gamma + 228195497348292395583004052225432529880555443978240*alpha**5*beta**4*delta**91*gamma - 1597368481438046769081028365578027709163888107847680*alpha**3*beta**6*delta**91*gamma + 2814411133962272878857049977447001201860183809064960*alpha*beta**8*delta**91*gamma + 12101276374530657341522942163469906887605212938240*alpha**6*beta**3*delta**90*gamma**2 - 285244371685365494478755065281790662350694304972800*alpha**4*beta**5*delta**90*gamma**2 + 1198026361078535076810771274183520781872916080885760*alpha**2*beta**7*delta**90*gamma**2 - 703602783490568219714262494361750300465045952266240*beta**9*delta**90*gamma**2 - 432188441947523476482962220123925245985900462080*alpha**8*delta**91*gamma**2 + 57048874337073098895751013056358132470138860994560*alpha**6*beta**2*delta**91*gamma**2 - 998355300898779230675642728486267318227430067404800*alpha**4*beta**4*delta**91*gamma**2 + 4925219484433977537999837460532252103255321665863680*alpha**2*beta**6*delta**91*gamma**2 - 6860127139033040142214059320027065429534198034595840*beta**8*delta**91*gamma**2 - 12101276374530657341522942163469906887605212938240*alpha**5*beta**4*delta**89*gamma**3 + 190162914456910329652503376854527108233796203315200*alpha**3*beta**6*delta**89*gamma**3 - 399342120359511692270257091394506927290972026961920*alpha*beta**8*delta**89*gamma**3 + 3457507535580187811863697760991401967887203696640*alpha**7*beta*delta**90*gamma**3 - 228195497348292395583004052225432529880555443978240*alpha**5*beta**3*delta**90*gamma**3 + 2396052722157070153621542548367041563745832161771520*alpha**3*beta**5*delta**90*gamma**3 - 56288222679245457577140999548
[…]

### 2022-07-05 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_16.py

@@ -1,1 +1,0 @@
-"1728753767790093905931848880495700983943601848320*alpha**6*beta*delta**93 - 60506381872653286707614710817349534438026064691200*alpha**4*beta**3*delta**93 + 447747225857634321636348860048386554841392878714880*alpha**2*beta**5*delta**93 - 831530562307035168753219311518432173276872489041920*beta**7*delta**93 - 5186261303370281717795546641487102951830805544960*alpha**5*beta**2*delta**92*gamma + 121012763745306573415229421634699068876052129382400*alpha**3*beta**4*delta**92*gamma - 447747225857634321636348860048386554841392878714880*alpha*beta**6*delta**92*gamma + 6482826629212852147244433301858878689788506931200*alpha**4*beta**3*delta**91*gamma**2 - 90759572808979930061422066226024301657039097036800*alpha**2*beta**5*delta**91*gamma**2 + 111936806464408580409087215012096638710348219678720*beta**7*delta**91*gamma**2 - 432188441947523476482962220123925245985900462080*alpha**6*delta**92*gamma**2 + 45379786404489965030711033113012150828519548518400*alpha**4*beta**2*delta**92*gamma**2 - 559684032322042902045436075060483193551741098393600*alpha**2*beta**4*delta**92*gamma**2 + 1455178484037311545318133795157256303234526855823360*beta**6*delta**92*gamma**2 - 4321884419475234764829622201239252459859004620800*alpha**3*beta**4*delta**90*gamma**3 + 30253190936326643353807355408674767219013032345600*alpha*beta**6*delta**90*gamma**3 + 2593130651685140858897773320743551475915402772480*alpha**5*beta*delta**91*gamma**3 - 121012763745306573415229421634699068876052129382400*alpha**3*beta**3*delta**91*gamma**3 + 671620838786451482454523290072579832262089318072320*alpha*beta**5*delta**91*gamma**3 + 1620706657303213036811108325464719672447126732800*alpha**2*beta**5*delta**89*gamma**4 - 3781648867040830419225919426084345902376629043200*beta**7*delta**89*gamma**4 - 4862119971909639110433324976394159017341380198400*alpha**4*beta**2*delta**90*gamma**4 + 113449466011224912576777582782530377071298871296000*alpha**2*beta**4*delta**90*gamma**4 - 195889411312715015715902626271169117743109384437760*beta**6*delta**90*gamma**4 - 11344946601122491257677758278253037707129887129600*a
[…]

### 2022-07-05 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_17.py

@@ -1,1 +1,0 @@
-"1220296777263595698304834503879318341607248363520*alpha**4*beta*delta**94 - 30100653839168693891519251095689852426312126300160*alpha**2*beta**3*delta**94 + 117392549972757906176925079273190424462617292570624*beta**5*delta**94 - 2440593554527191396609669007758636683214496727040*alpha**3*beta**2*delta**93*gamma + 30100653839168693891519251095689852426312126300160*alpha*beta**4*delta**93*gamma + 1830445165895393547457251755818977512410872545280*alpha**2*beta**3*delta**92*gamma**2 - 7525163459792173472879812773922463106578031575040*beta**5*delta**92*gamma**2 - 305074194315898924576208625969829585401812090880*alpha**4*delta**93*gamma**2 + 22575490379376520418639438321767389319734094725120*alpha**2*beta**2*delta**93*gamma**2 - 146740687465947382721156349091488030578271615713280*beta**4*delta**93*gamma**2 - 610148388631797849152417251939659170803624181760*alpha*beta**4*delta**91*gamma**3 + 1220296777263595698304834503879318341607248363520*alpha**3*beta*delta**92*gamma**3 - 30100653839168693891519251095689852426312126300160*alpha*beta**3*delta**92*gamma**3 + 76268548578974731144052156492457396350453022720*beta**5*delta**90*gamma**4 - 1372833874421545160592938816864233134308154408960*alpha**2*beta**2*delta**91*gamma**4 + 9406454324740216841099765967403078883222539468800*beta**4*delta**91*gamma**4 - 5643872594844130104659859580441847329933523681280*alpha**2*beta*delta**92*gamma**4 + 73370343732973691360578174545744015289135807856640*beta**3*delta**92*gamma**4 + 610148388631797849152417251939659170803624181760*alpha*beta**3*delta**90*gamma**5 - 152537097157949462288104312984914792700906045440*alpha**3*delta**91*gamma**5 + 11287745189688260209319719160883694659867047362560*alpha*beta**2*delta**91*gamma**5 - 95335685723718413930065195615571745438066278400*beta**4*delta**89*gamma**6 + 343208468605386290148234704216058283577038602240*alpha**2*beta*delta**90*gamma**6 - 4703227162370108420549882983701539441611269734400*beta**3*delta**90*gamma**6 + 470322716237010842054988298370153944161126973440*alpha**2*delta**91*gamma**6 - 1834258593324342284014454363643600382228395
[…]

### 2022-07-05 archived/output_mathematica_coefficients/numerator/rationalNumerator_coefficients_18.py

@@ -1,1 +1,0 @@
-"542354123228264754802148668390808151825443717120*alpha**2*beta*delta**95 - 7050603601967441812427932689080505973730768322560*beta**3*delta**95 - 542354123228264754802148668390808151825443717120*alpha*beta**2*delta**94*gamma + 135588530807066188700537167097702037956360929280*beta**3*delta**93*gamma**2 - 135588530807066188700537167097702037956360929280*alpha**2*delta**94*gamma**2 + 5287952701475581359320949516810379480298076241920*beta**2*delta**94*gamma**2 + 271177061614132377401074334195404075912721858560*alpha*beta*delta**93*gamma**3 - 101691398105299641525402875323276528467270696960*beta**2*delta**92*gamma**4 - 1321988175368895339830237379202594870074519060480*beta*delta**93*gamma**4 - 33897132701766547175134291774425509489090232320*alpha*delta**92*gamma**5 + 25422849526324910381350718830819132116817674240*beta*delta**91*gamma**6 + 110165681280741278319186448266882905839543255040*delta**92*gamma**6 - 2118570793860409198445893235901594343068139520*delta**90*gamma**8 + 20609456682674060682481649398850709769366861250560*alpha**2*delta**95.5*H - 846072432236093017491351922689660716847692198707200*beta**2*delta**95.5*H - 20609456682674060682481649398850709769366861250560*alpha*beta*delta**94.5*gamma*H + 1084708246456529509604297336781616303650887434240*alpha*delta**95.5*gamma*H + 5152364170668515170620412349712677442341715312640*beta**2*delta**93.5*gamma**2*H + 422493861994818243990873812676439550272020655636480*beta*delta**94.5*gamma**2*H + 5152364170668515170620412349712677442341715312640*alpha*delta**93.5*gamma**3*H - 2576182085334257585310206174856338721170857656320*beta*delta**92.5*gamma**4*H - 52743938483948747404508958001006092765024401489920*delta**93.5*gamma**4*H + 322022760666782198163775771857042340146357207040*delta**91.5*gamma**6*H - 33018519022136758272354810931632400283133013498265600*beta*delta**96*H**2 - 26032997914956708230503136082758791287621298421760*delta**97*H**2 + 8254629755534189568088702732908100070783253374566400*delta**95*gamma**2*H**2 - 418784159791936913068027115784646422513534620611379200*delta**96.5*H**3"

### 2022-07-05 bash_scripts/main.sh
Delete bash_scripts directory

@@ -1,18 +1,0 @@
-# RUN IN PARALLEL ON MULTIPLE CPUS
-
-parallel --bar python src/engine/main.py \
-    --atom1 {1} \
-    --atom2 {1} \
-    --r 0.5 1.0 1.5 2.0 2.5 3.0 \
-    --tau 0.0 1.0 2.0 \
-    --energy_unit hartree \
-    --n_eigenvalues 1 \
-    ::: H Li K Rb Cs He Ne Ar Kr Xe
-
-#parallel --bar python src/engine/main.py \
-#    --atom1 {1} \
-#    --atom2 {1} \
-#    --r 0.5 1.0 1.5 2.0 2.5 3.0 \
-#    --tau 0.0 \
-#    --energy_unit hartree \
-#    ::: H

### 2022-07-05 bash_scripts/test.sh

@@ -1,7 +1,0 @@
-python src/engine/main.py \
-    --atom1 H \
-    --atom2 H \
-    --r 0.8 0.9 1. 1.1 1.2 1.3 1.4 1.5 1.6 1.7 1.8 1.9 2. 2.1 2.2 2.3 2.4 2.5 2.6 2.7 2.8 2.9 3. 3.1 3.2 3.3 3.4 3.5 3.6 3.7 3.8 3.9 4. 4.1 4.2 4.3 4.4 4.5 4.6  \
-    --tau 0.2 \
-    --energy_unit hartree \
-    --n_eigenvalues 3

### 2022-07-06 src/expansion_coefficients/N_20/coefficients_array.py
clean up

@@ -1,7 +1,7 @@
 import numpy as np
 
-from src.engine.expansion_coefficients.N_20.numerator.rationalNumerator_coefficients import *
-from src.engine.expansion_coefficients.N_20.denominator.rationalDenominator_coefficients import *
+from src.expansion_coefficients.N_20.numerator.rationalNumerator_coefficients import *
+from src.expansion_coefficients.N_20.denominator.rationalDenominator_coefficients import *
 
 def numerator_coefficients_array(
 	alpha: float,

### 2022-07-06 src/gui/test2.py

@@ -1,96 +1,0 @@
-# -*- coding: utf-8 -*-
-
-# Form implementation generated from reading ui file 'src/gui/test.ui'
-#
-# Created by: PyQt5 UI code generator 5.15.4
-#
-# WARNING: Any manual changes made to this file will be lost when pyuic5 is
-# run again.  Do not edit this file unless you know what you are doing.
-
-
-from PyQt5 import QtCore, QtGui, QtWidgets
-
-
-class Ui_MainWindow(object):
-    def setupUi(self, MainWindow):
-        MainWindow.setObjectName("MainWindow")
-        MainWindow.resize(800, 600)
-
-        self.centralwidget = QtWidgets.QWidget(MainWindow)
-        self.centralwidget.setObjectName("centralwidget")
-        self.label = QtWidgets.QLabel(self.centralwidget)
-        self.label.setGeometry(QtCore.QRect(170, 100, 481, 211))
-
-        font = QtGui.QFont()
-        font.setPointSize(36)
-        self.label.setFont(font)
-        self.label.setObjectName("label")
-
-        MainWindow.setCentralWidget(self.centralwidget)
-
-        self.menubar = QtWidgets.QMenuBar(MainWindow)
-        self.menubar.setGeometry(QtCore.QRect(0, 0, 800, 22))
-        self.menubar.setObjectName("menubar")
-        self.menuFile = QtWidgets.QMenu(self.menubar)
-        self.menuFile.setObjectName("menuFile")
-        self.menuEdit = QtWidgets.QMenu(self.menubar)
-        self.menuEdit.setObjectName("menuEdit")
-        MainWindow.setMenuBar(self.menubar)
-        self.statusbar = QtWidgets.QStatusBar(MainWindow)
-        self.statusbar.setObjectName("statusbar")
-        MainWindow.setStatusBar(self.statusbar)
-        self.actionNew = QtWidgets.QAction(MainWindow)
-        self.actionNew.setObjectName("actionNew")
-        self.actionSave = QtWidgets.QAction(MainWindow)
-        self.actionSave.setObjectName("actionSave")
-        self.actionCopy = QtWidgets.QAction(MainWindow)
-        self.actionCopy.setObjectName("actionCopy")
-        self.actionPaste = QtWidgets.QAction(MainWindow)
-        self.actionPaste.setObjectName("actionPaste")
-        self.menuFile.addAction(self.actionNew)
-        self.menuFile.addAction(self.actionSave)
[…]

### 2022-07-06 src/main.py

@@ -1,7 +1,7 @@
 from argparse import ArgumentParser
 import os
 
-from src.engine.solver import Solver
+from src.solver import Solver
 
 def main(args) -> None:
 

### 2022-07-06 src/solver.py

@@ -7,9 +7,9 @@ from typing import Dict, List
 import warnings
 warnings.filterwarnings("error")
 
-from src.engine.expansion_coefficients.N_20.coefficients_array import *
-from src.engine.couplings import *
-from src.engine.utils.atomic_data import *
+from src.expansion_coefficients.N_20.coefficients_array import *
+from src.couplings import *
+from src.utils.atomic_data import *
 
 class Solver():
 
